\begin{filecontents}{revision_supplement.aux}
\relax 
\providecommand\hyper@newdestlabel[2]{}
\providecommand\HyperFirstAtBeginDocument{\AtBeginDocument}
\HyperFirstAtBeginDocument{\ifx\hyper@anchor\@undefined
	\global\let\oldcontentsline\contentsline
	\gdef\contentsline#1#2#3#4{\oldcontentsline{#1}{#2}{#3}}
	\global\let\oldnewlabel\newlabel
	\gdef\newlabel#1#2{\newlabelxx{#1}#2}
	\gdef\newlabelxx#1#2#3#4#5#6{\oldnewlabel{#1}{{#2}{#3}}}
	\AtEndDocument{\ifx\hyper@anchor\@undefined
		\let\contentsline\oldcontentsline
		\let\newlabel\oldnewlabel
		\fi}
	\fi}
\global\let\hyper@last\relax 
\gdef\HyperFirstAtBeginDocument#1{#1}
\providecommand\HyField@AuxAddToFields[1]{}
\providecommand\HyField@AuxAddToCoFields[2]{}
\citation{HeldEtAl1985}
\citation{CapetEtAl2008}
\newlabel{app:sqg}{{SM1}{SM1}{Supplement to \cref {sec:metricLearning}: metric-learning with the surface quasi--\\geostrophic equation}{section.1}{}}
\newlabel{app:sqg@cref}{{[section][1][]SM1}{[SM1][1][]SM1}}
\@writefile{toc}{\contentsline {section}{\numberline {SM1}Supplement to \cref  {sec:metricLearning}: metric-learning with the surface quasi--\\geostrophic equation}{SM1}{figure.caption.2}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.1}Experimental setup}{SM1}{subsection.3}\protected@file@percent }
\newlabel{eq:sqg_system}{{SM1.1}{SM1}{Experimental setup}{equation.4}{}}
\newlabel{eq:sqg_system@cref}{{[equation][1][1]SM1.1}{[SM1][1][]SM1}}
\@writefile{lof}{\contentsline {figure}{\numberline {SM1}{\ignorespaces Examples of buoyancy, evolving according to \cref  {eq:sqg_system}, at initial (top) and final time (bottom) for ${\bm  {\theta }}$ sampled from class $i = 0$ (left) and $i = 1$ (right). Observations consist of solution values at nine spatial locations in the domain, as depicted in plots (c) and (d). We use the observations to estimate a metric which will distinguish between solutions corresponding to ${\bm  {\theta }}$ sampled from class $i = 0$ and ${\bm  {\theta }}$ sampled from class $i = 1$. \relax }}{SM2}{figure.caption.2}\protected@file@percent }
\providecommand*\caption@xref[2]{\@setref\relax\@undefined{#1}}
\newlabel{fig:SQG_solution}{{SM1}{SM2}{Examples of buoyancy, evolving according to \cref {eq:sqg_system}, at initial (top) and final time (bottom) for $\bftheta $ sampled from class $i = 0$ (left) and $i = 1$ (right). Observations consist of solution values at nine spatial locations in the domain, as depicted in plots (c) and (d). We use the observations to estimate a metric which will distinguish between solutions corresponding to $\bftheta $ sampled from class $i = 0$ and $\bftheta $ sampled from class $i = 1$. \relax }{figure.caption.2}{}}
\newlabel{fig:SQG_solution@cref}{{[figure][1][]SM1}{[SM1][1][]SM2}}
\newlabel{app:sqg:addResults}{{SM1.2}{SM3}{Additional results}{subsection.5}{}}
\newlabel{app:sqg:addResults@cref}{{[subsection][2][1]SM1.2}{[SM1][3][]SM3}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.2}Additional results}{SM3}{subsection.5}\protected@file@percent }
\@writefile{lof}{\contentsline {figure}{\numberline {SM2}{\ignorespaces \textbf  {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat  \Gamma _0^{\rm  LF}$, $\hat  \Gamma _0^{\rm  EMF}$, $\hat  \Gamma _0^{\rm  LEMF}$, and $\hat  \Gamma _0^{\rm  MRMF}$ compared to that of $\hat  \Gamma _0^{\rm  HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat  \Gamma _0^{\rm  HF}$. \textbf  {Bottom:} Frobenius squared error histograms of $\hat  \Gamma _0^{\rm  LF}$ (left), $\hat  \Gamma _0^{\rm  EMF}$ (center), and $\hat  \Gamma _0^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _0^{\rm  MRMF}$, overlaid in blue. In the Frobenius metric $\hat  \Gamma _{\rm  0}^{\rm  EMF}$ is the best-performing estimator, which is to be expected, as $\hat  \Gamma _{\rm  0}^{\rm  EMF}$ is optimized to minimize Frobenius MSE. . \relax }}{SM3}{figure.caption.6}\protected@file@percent }
\newlabel{fig:Gamma0_fro}{{SM2}{SM3}{\textbf {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat \Gamma _0^{\rm LF}$, $\hat \Gamma _0^{\rm EMF}$, $\hat \Gamma _0^{\rm LEMF}$, and $\hat \Gamma _0^{\rm MRMF}$ compared to that of $\hat \Gamma _0^{\rm HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat \Gamma _0^{\rm HF}$. \textbf {Bottom:} Frobenius squared error histograms of $\hat \Gamma _0^{\rm LF}$ (left), $\hat \Gamma _0^{\rm EMF}$ (center), and $\hat \Gamma _0^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _0^{\rm MRMF}$, overlaid in blue. In the Frobenius metric $\hat \Gamma _{\rm 0}^{\rm EMF}$ is the best-performing estimator, which is to be expected, as $\hat \Gamma _{\rm 0}^{\rm EMF}$ is optimized to minimize Frobenius MSE. . \relax }{figure.caption.6}{}}
\newlabel{fig:Gamma0_fro@cref}{{[figure][2][]SM2}{[SM1][3][]SM3}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {SM1.2.1}Estimation of $\Gamma _0$}{SM4}{subsubsection.7}\protected@file@percent }
\@writefile{lof}{\contentsline {figure}{\numberline {SM3}{\ignorespaces \textbf  {Top:} Intrinsic squared error histograms corresponding to $\hat  \Gamma _0^{\rm  LF}$ (left), $\hat  \Gamma _0^{\rm  LEMF}$ (center), and $\hat  \Gamma _0^{\rm  MRMF}$ (right). Squared error histograms for $\hat  \Gamma _0^{\rm  HF}$ are overlaid in cyan for comparison. Reported changes in MSE are relative to $\hat  \Gamma _0^{\rm  HF}$. \textbf  {Bottom:} Intrinsic squared error histograms of $\hat  \Gamma _0^{\rm  LF}$ (left) and $\hat  \Gamma _0^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _0^{\rm  MRMF}$, overlaid in blue. Use of $\hat  \Gamma _0^{\rm  MRMF}$ results in an 31\% decrease in intrinsic MSE relative to that of $\hat  \Gamma _0^{\rm  LF}$ and a 76\% decrease relative to that of $\hat  \Gamma _0^{\rm  LEMF}$. We do not report results for $\hat  \Gamma _{0}^{\rm  EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 82.4\% of its realizations are indefinite. \relax }}{SM4}{figure.caption.8}\protected@file@percent }
\newlabel{fig:Gamma0_AI_LE}{{SM3}{SM4}{\textbf {Top:} Intrinsic squared error histograms corresponding to $\hat \Gamma _0^{\rm LF}$ (left), $\hat \Gamma _0^{\rm LEMF}$ (center), and $\hat \Gamma _0^{\rm MRMF}$ (right). Squared error histograms for $\hat \Gamma _0^{\rm HF}$ are overlaid in cyan for comparison. Reported changes in MSE are relative to $\hat \Gamma _0^{\rm HF}$. \textbf {Bottom:} Intrinsic squared error histograms of $\hat \Gamma _0^{\rm LF}$ (left) and $\hat \Gamma _0^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _0^{\rm MRMF}$, overlaid in blue. Use of $\hat \Gamma _0^{\rm MRMF}$ results in an 31\% decrease in intrinsic MSE relative to that of $\hat \Gamma _0^{\rm LF}$ and a 76\% decrease relative to that of $\hat \Gamma _0^{\rm LEMF}$. We do not report results for $\hat \Gamma _{0}^{\rm EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 82.4\% of its realizations are indefinite. \relax }{figure.caption.8}{}}
\newlabel{fig:Gamma0_AI_LE@cref}{{[figure][3][]SM3}{[SM1][4][]SM4}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {SM1.2.2}Estimation of $\Gamma _1$}{SM4}{subsubsection.9}\protected@file@percent }
\@writefile{lof}{\contentsline {figure}{\numberline {SM4}{\ignorespaces \textbf  {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat  \Gamma _1^{\rm  LF}$, $\hat  \Gamma _1^{\rm  EMF}$, $\hat  \Gamma _1^{\rm  LEMF}$, and $\hat  \Gamma _1^{\rm  MRMF}$ compared to that of $\hat  \Gamma _1^{\rm  HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat  \Gamma _1^{\rm  HF}$. \textbf  {Bottom:} Frobenius squared error histograms of $\hat  \Gamma _1^{\rm  LF}$ (left), $\hat  \Gamma _1^{\rm  EMF}$ (center), and $\hat  \Gamma _1^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _1^{\rm  MRMF}$, overlaid in blue. All four estimators obtain substantial decreases in MSE relative to $\hat  \Gamma _1^{\rm  HF}$, but, interestingly, in the Frobenius metric $\hat  \Gamma _1^{\rm  MRMF}$ achieves the smallest reduction. By contrast, $\hat  \Gamma _1^{\rm  MRMF}$ is the best-performing estimator in the intrinsic metric (\cref  {fig:Gamma1_AI_LE}). \relax }}{SM5}{figure.caption.10}\protected@file@percent }
\newlabel{fig:Gamma1_fro}{{SM4}{SM5}{\textbf {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat \Gamma _1^{\rm LF}$, $\hat \Gamma _1^{\rm EMF}$, $\hat \Gamma _1^{\rm LEMF}$, and $\hat \Gamma _1^{\rm MRMF}$ compared to that of $\hat \Gamma _1^{\rm HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat \Gamma _1^{\rm HF}$. \textbf {Bottom:} Frobenius squared error histograms of $\hat \Gamma _1^{\rm LF}$ (left), $\hat \Gamma _1^{\rm EMF}$ (center), and $\hat \Gamma _1^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _1^{\rm MRMF}$, overlaid in blue. All four estimators obtain substantial decreases in MSE relative to $\hat \Gamma _1^{\rm HF}$, but, interestingly, in the Frobenius metric $\hat \Gamma _1^{\rm MRMF}$ achieves the smallest reduction. By contrast, $\hat \Gamma _1^{\rm MRMF}$ is the best-performing estimator in the intrinsic metric (\cref {fig:Gamma1_AI_LE}). \relax }{figure.caption.10}{}}
\newlabel{fig:Gamma1_fro@cref}{{[figure][4][]SM4}{[SM1][4][]SM5}}
\@writefile{lof}{\contentsline {figure}{\numberline {SM5}{\ignorespaces \textbf  {Top:} Intrinsic squared error histograms corresponding to $\hat  \Gamma _1^{\rm  LF}$ (left), $\hat  \Gamma _1^{\rm  LEMF}$ (center), and $\hat  \Gamma _1^{\rm  MRMF}$ (right). Squared error histograms corresponding to $\hat  \Gamma _1^{\rm  HF}$ are overlaid in cyan on each plot for comparison. Changes in MSE are relative to $\hat  \Gamma _1^{\rm  HF}$. \textbf  {Bottom:} Intrinsic squared error histograms of $\hat  \Gamma _1^{\rm  LF}$ (left) and $\hat  \Gamma _1^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _1^{\rm  MRMF}$, overlaid in blue. Use of $\hat  \Gamma _1^{\rm  MRMF}$ results in a 49\% decrease in intrinsic MSE relative to $\hat  \Gamma _1^{\rm  LF}$ and a 66\% decrease relative to $\hat  \Gamma _1^{\rm  LEMF}$. We do not report results for $\hat  \Gamma _{1}^{\rm  EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 67\% of its realizations are indefinite\relax }}{SM6}{figure.caption.11}\protected@file@percent }
\newlabel{fig:Gamma1_AI_LE}{{SM5}{SM6}{\textbf {Top:} Intrinsic squared error histograms corresponding to $\hat \Gamma _1^{\rm LF}$ (left), $\hat \Gamma _1^{\rm LEMF}$ (center), and $\hat \Gamma _1^{\rm MRMF}$ (right). Squared error histograms corresponding to $\hat \Gamma _1^{\rm HF}$ are overlaid in cyan on each plot for comparison. Changes in MSE are relative to $\hat \Gamma _1^{\rm HF}$. \textbf {Bottom:} Intrinsic squared error histograms of $\hat \Gamma _1^{\rm LF}$ (left) and $\hat \Gamma _1^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _1^{\rm MRMF}$, overlaid in blue. Use of $\hat \Gamma _1^{\rm MRMF}$ results in a 49\% decrease in intrinsic MSE relative to $\hat \Gamma _1^{\rm LF}$ and a 66\% decrease relative to $\hat \Gamma _1^{\rm LEMF}$. We do not report results for $\hat \Gamma _{1}^{\rm EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 67\% of its realizations are indefinite\relax }{figure.caption.11}{}}
\newlabel{fig:Gamma1_AI_LE@cref}{{[figure][5][]SM5}{[SM1][6][]SM6}}
\citation{pennec2006intrinsic}
\newlabel{app:prodMan}{{SM2}{SM7}{SPD Product Manifolds}{section.12}{}}
\newlabel{app:prodMan@cref}{{[section][2][]SM2}{[SM1][7][]SM7}}
\@writefile{toc}{\contentsline {section}{\numberline {SM2}SPD Product Manifolds}{SM7}{section.12}\protected@file@percent }
\newlabel{app:prodMan_geom}{{SM2.1}{SM7}{Geometry}{subsection.13}{}}
\newlabel{app:prodMan_geom@cref}{{[subsection][1][2]SM2.1}{[SM1][7][]SM7}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM2.1}Geometry}{SM7}{subsection.13}\protected@file@percent }
\newlabel{eq:geodesicPnK}{{SM2.1}{SM7}{Geometry}{equation.14}{}}
\newlabel{eq:geodesicPnK@cref}{{[equation][1][2]SM2.1}{[SM1][7][]SM7}}
\bibstyle{siamplain}
\bibdata{references}
\bibcite{CapetEtAl2008}{1}
\bibcite{HeldEtAl1985}{2}
\bibcite{pennec2006intrinsic}{3}
\newlabel{app:prodMan_stats}{{SM2.2}{SM8}{Statistics}{subsection.15}{}}
\newlabel{app:prodMan_stats@cref}{{[subsection][2][2]SM2.2}{[SM1][7][]SM8}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM2.2}Statistics}{SM8}{subsection.15}\protected@file@percent }
\newlabel{eq:prodman_mean}{{SM2.2}{SM8}{Statistics}{equation.16}{}}
\newlabel{eq:prodman_mean@cref}{{[equation][2][2]SM2.2}{[SM1][8][]SM8}}
\newlabel{eq:prodMan}{{SM2.3}{SM8}{Statistics}{equation.17}{}}
\newlabel{eq:prodMan@cref}{{[equation][3][2]SM2.3}{[SM1][8][]SM8}}
\gdef \@abspage@last{8}
\end{filecontents}