\documentclass{aa}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%
% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{txfonts}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}        % Multi-column entries in tables
\usepackage{bm}		% Bold maths symbols, including upright Greek
\usepackage{pdflscape}	% Landscape pages
\usepackage{color} % colored text
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{csquotes}
\usepackage[
  locale=US,
  separate-uncertainty=true,
  per-mode=symbol-or-fraction,
  range-phrase=-,
]{siunitx}
\usepackage{multirow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%% AUTHORS - PLACE YOUR OWN MACROS HERE %%%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
\newcommand{\kms}{\,km\,s$^{-1}$} % kilometres per second
\newcommand{\bibtex}{\textsc{Bib}\!\TeX} % bibtex. Not quite the correct typesetting, but close enough
\newcommand\FilterDeep{\texttt{Filter Deep}}
\newcommand\uv[1]{$(u, v)$ #1}
\newcommand\lm[1]{$(l, m)$ #1}

\DeclareSIUnit{\arbitraryunit}{a.u.}
\DeclareSIUnit{\gigabyte}{GB}
\DeclareSIUnit{\pixel}{px}
\DeclareSIUnit{\jansky}{Jy}

\makeatletter
\renewcommand*\aa@pageof{, page \thepage{} of \pageref*{LastPage}}
\makeatother

\newenvironment{absolutelynopagebreak}
  {\par\nobreak\vfil\penalty0\vfilneg
   \vtop\bgroup}
  {\par\xdef\tpd{\the\prevdepth}\egroup
   \prevdepth=\tpd}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
\renewcommand{\figureautorefname}{Fig.}
\renewcommand{\tableautorefname}{Tab.}
\renewcommand{\sectionautorefname}{Sect.}
\renewcommand{\equationautorefname}{Eq.}

   \title{Deep learning-based radiointerferometric imaging with GAN-aided training}
   
   \author{
    K. Schmidt\inst{1}\thanks{Contact e-mail: \href{mailto:kevin3.schmidt@tu-dortmund.de}{kevin3.schmidt@tu-dortmund.de}},
    F. Geyer\inst{1}\thanks{Contact e-mail: \href{mailto:felix.geyer@tu-dortmund.de}{felix.geyer@tu-dortmund.de}},
    J. Kummer\inst{2,3},
    M. Brüggen\inst{2},
    H.~W.~Edler\inst{2},
    D. Elsässer\inst{1},
    F.~Griese\inst{3,4,5},
    A.~Poggenpohl\inst{1},
    L.~Rustige\inst{3,6}
    \and
    W. Rhode\inst{1}
    }

   \institute{Astroparticle Physics, TU Dortmund University,
              Otto-Hahn-Stra{\ss}e 4a, 44227 Dortmund, Germany
         \and
             Hamburger Sternwarte, University of Hamburg,
             Gojenbergsweg 112, 21029 Hamburg, Germany
        \and
            Center for Data and Computing in Natural Sciences (CDCS), Notkestrasse 9, 22607 Hamburg, Germany
        \and 
            Section for Biomedical Imaging, University Medical Center Hamburg-Eppendorf, D-20246 Hamburg, Germany
        \and 
            Institute for Biomedical Imaging, Hamburg University of Technology, D-21073 Hamburg, Germany
        \and 
            Deutsches Elektronen-Synchrotron DESY, Notkestra{\ss}e 85, D-22607 Hamburg, Germany
            }
   \date{Received ; accepted }

% \abstract{}{}{}{}{} 
% 5 {} token are mandatory
 
  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {Radio interferometry invariably suffers from an incomplete coverage of the spatial Fourier space, which leads to imaging artifacts. The current state-of-the-art technique is to create an image by Fourier-transforming the incomplete visibility data and to clean the systematic effects originating from incomplete data in Fourier space. Previously, we have shown how super-resolution methods based on convolutional neural networks can reconstruct sparse visibility data. 
   }
  % aims heading (mandatory)
   {Our previous work has suffered from a low realism of the training data. The aim of this work is to build a whole simulation chain for realistic radio sources that then leads to a vastly improved neural net for the reconstruction of missing visibilities. This method offers considerable improvements in terms of speed, automatization and reproducibility over the standard techniques.}
  % methods heading (mandatory)
   {Here we generate large amounts of training data by creating images of radio galaxies with a generative adversarial network (GAN) that has been trained on radio survey data. Then, we applied the Radio Interferometer Measurement Equation (RIME) in order to simulate the measurement process of a radio interferometer.}
  % results heading (mandatory)
   {We show that our neural network can reconstruct faithfully images of  realistic radio galaxies. The reconstructed images agree well with the original images in terms of the source area, integrated flux density, peak flux density, and the multi-scale structural similarity index. Finally, we show how the neural net can be adapted to estimate the uncertainties in the imaging process.}
  % conclusions heading (optional), leave it empty if necessary 
   {}

   \keywords{Galaxies: active -- Radio continuum: galaxies -- Methods: data analysis -- Techniques: image processing -- Techniques: interferometric
               }

   \titlerunning{Deep learning-based radiointerferometric imaging with GAN-aided training}
   \authorrunning{Schmidt et al.}
   \maketitle

\input{01_introduction.tex}
\input{02_gan_simulations.tex}
\input{03_rime.tex}
\input{04_model_training.tex}
\input{05_evaluation.tex}
\input{06_future_work.tex}
\input{07_conclusions.tex}
\input{08_acknowledgments.tex}

\bibliographystyle{aa}
\bibliography{references}

\FloatBarrier
\input{09_appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}


