\section{Broader Applications and Future Work}\label{sec:future}
\ours unlocks opportunities for many exciting venues.

\paragraph{Human-in-the-loop Web Navigation} 
In our intent collection, we deliberately keep all under-specified intents, which without further user specification, are impossible to complete.
These examples highlight the importance of involving humans in the task completion process~\citep{nguyen_help_2019,nguyen2022hari}.  


\paragraph{Learning by Reading External Knowledge} Our benchmark offers a rich collection of external knowledge resources that can facilitate learning by reading, in addition to trial and error~\citep{branavan2012learning,zhong2019rtfm, zhou2022docprompting}. To successfully perform tasks, humans often refer to relevant materials such as user manuals or instructional videos. Our benchmark provides extensive resources in text and video format for each platform, allowing researchers to explore the potential of building intelligent agents with strong reading comprehension capabilities. Furthermore, our experiments demonstrate the effectiveness of leveraging external knowledge, highlighting the potential for further research in this area.

\paragraph{Optimize Web Navigation Agents for Different Roles} 
Even on the same website, people with different roles will use different functionalities, and their trajectories may exhibit unique features. 
To account for this, we explicitly annotate the potential roles of the trajectories in our benchmark and perform a break-down evaluation on each role. 
For example, in our GitLab tasks, we model the roles such as professional developers, group managers. 
This role annotation allows for a more nuanced evaluation of web navigation agents and can help researchers to design agents that are optimized for specific roles and use cases.