% Appendix B

\chapter*{Publications of the Author} % Main appendix title
\label{AppendixB} % For referencing this appendix elsewhere, use \ref{AppendixA}
\addcontentsline{toc}{chapter}{Publications of the Author}
\markboth{Publications of the Author}{Publications of the Author}

The research works carried out for the completion of this thesis work have resulted in several publications in national conferences, international conferences, book chapter, and specialized journals. We present these publications next, sorting them by publication type.

\section*{International journals (\#5)}


\textbf{M. Sarrouti}, S. O. E. Alaoui, A machine learning-based method for question type classification in biomedical question answering, Methods of Information in Medicine 56 (3) (2017) 209-216, \url{https://doi.org/10.3414/ME16-01-0116}.

\textbf{M. Sarrouti}, A. Lachkar, A new and efficient method based on syntactic dependency relations features for ad hoc clinical question classification, International Journal of Bioinformatics Research and Applications 13 (2) (2017) 161–177, \url{https://doi.org/10.1504/IJBRA.2017.10003490}.

\textbf{M. Sarrouti}, S. O. E. Alaoui, A passage retrieval method based on probabilistic information retrieval and UMLS concepts in biomedical question answering, Journal of Biomedical Informatics 68 (2017) 96–103, \url{https://doi.org/10.1016/j.jbi.2017.03.001}.

\textbf{M. Sarrouti}, S. O. E. Alaoui, A yes/no answer generator based on sentiment-word scores in biomedical question answering, International Journal of Healthcare Information Systems and Informatics 12 (3) (2017) 62–74, \url{https://doi.org/10.4018/ijhisi.2017070104}.

\textbf{M. Sarrouti}, S. O. E. Alaoui, SemBioNLQA: A semantic biomedical question answering system for retrieving exact and ideal answers to natural language questions, Artificial Intelligence in Medicine (\textbf{submitted}).

\section*{Book chapter (\#1)}

\textbf{M. Sarrouti}, S. O. E. Alaoui, A generic document retrieval framework based on UMLS similarity for biomedical question answering system, In: Czarnowski I., Caballero A., Howlett R., Jain L. (eds) Intelligent Decision Technologies 2016, Smart Innovation, Systems and Technologies 57 (2016) 207–216, \url{https://doi.org/10.1007/978-3-319-39627-9_18}. Springer, Cham.


\section*{International conferences and workshops (\#3)}

\textbf{M. Sarrouti}, S. O. E. Alaoui, A biomedical question answering system in BioASQ 2017, in: BioNLP 2017, Association for Computational Linguistics, 2017, \url{https://doi.org10.18653/v1/w17-2337}, July 30-August 4, 2017 Vancouver, Canada.

\textbf{M. Sarrouti,} S. O. E. Alaoui, A generic document retrieval framework based on UMLS similarity for biomedical question answering system, In: The 8th KES International Conference on Intelligent Decision Technologies (KES-IDT 2016), 2016, Volume 57, pp. 207–216; doi: \url{https://doi.org/10.1007/978-3-319-39627-9\_18}, June 15-17, 2016, Tenerife, Spain.


\textbf{M. Sarrouti}, A. Lachkar, S. O. E. Alaoui, Biomedical question types classification using syntactic and rule based approach, in: Proceedings of the 7th International Joint Conference on Knowledge Discovery, Knowledge Engineering and Knowledge Management, 2015, Volume 1: KDIR, pp. 265–272. ISBN 978-989-758-158-8; doi: \url{http://dx.doi.org/10.5220/0005598002650272}, November 12-14, 2015, Lisbon, Portugal.

\section*{National conferences (\#2)}

\textbf{M. Sarrouti}, S. O. E. Alaoui, Recherche de réponses précises à des questions biomédicales : système de questions-réponses, In: Signal, ImaGe, Multimédia et Applications (SIGMA), December 21-22, 2016, Fez, Morocco.

\textbf{M. Sarrouti}, A. A. Hassani, I. E. Bellili, A. Lachkar, S. O. E. Alaoui, Machine learning methods evaluation for biomedical named entities recognition, In: Les Journes Doctorales en Technologies de l'Information et de la Communication (JDTIC’14), June 19-20, 2014, Rabat, Morocco.






