\author[L\'opez-Caraballo C. H. et al.]
{
{C. H. L\'opez-Caraballo$^{\orcidlink{0000-0002-6439-5385}}$,$^{1,2}$} \thanks{E-mail: clopez@iac.es, lopezcaraballoch@gmail.com}
{B. Ruiz-Granados$^{\orcidlink{0000-0003-3229-2725}}$,$^{3}$} %{B. Ruiz-Granados$^{\orcidlink{0000-0003-3229-2725}}$,$^{1,2,14}$}
{R.~T. G\'{e}nova-Santos$^{\orcidlink{0000-0001-5479-0034}}$,$^{1,2}$}
\newauthor
{M. Fern\'{a}ndez-Torreiro$^{\orcidlink{0000-0002-6805-9100}}$,$^{1,2}$}
{J.~A. Rubi\~{n}o-Mart\'{\i}n$^{\orcidlink{0000-0001-5289-3021}}$,$^{1,2}$}
{M.~W. Peel$^{\orcidlink{0000-0003-3412-2586}}$,$^{4,1,2}$}
{F. Poidevin$^{\orcidlink{0000-0002-5391-5568}}$,$^{1,2}$}
%{F. Poidevin$^{\orcidlink{0000-0002-5391-5568}}$,$^{1,2}$}
\newauthor
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{E. Artal$^{\orcidlink{0000-0002-2569-1894}}$,$^{5}$} %{E. Artal$^{\orcidlink{0000-0002-2569-1894}}$,$^{5}$}
{M. Ashdown$^{\orcidlink{0000-0003-2044-7523}}$,$^{6,7}$} %{M. Ashdown$^{\orcidlink{0000-0003-2044-7523}}$,$^{6,7}$}
{R.~B. Barreiro$^{\orcidlink{0000-0002-6139-4272}}$,$^{8}$} % {R.~B. Barreiro$^{\orcidlink{0000-0002-6139-4272}}$,$^{8}$}
{F.~J. Casas$^{\orcidlink{0000-0002-2217-5843}}$,$^{8}$} %{F.~J. Casas$^{\orcidlink{0000-0002-2217-5843}}$,$^{8}$}
{E. de la Hoz$^{\orcidlink{0000-0002-5066-816X}}$,$^{8,9,10}$} %{E. de la Hoz$^{\orcidlink{0000-0002-5066-816X}}$,$^{8,9,10}$}
\newauthor
{R. Gonz\'alez-Gonz\'alez$^{1,2}$} %
{F. Guidi$^{\orcidlink{0000-0001-7593-3962}}$,$^{11}$} %{F. Guidi$^{\orcidlink{0000-0001-7593-3962}}$,$^{11}$}
{D. Herranz$^{\orcidlink{0000-0003-4540-1417}}$,$^{8}$} %{D. Herranz$^{\orcidlink{0000-0003-4540-1417}}$,$^{8}$}
{R. Hoyland$^{\orcidlink{0000-0001-5346-0519}}$,$^{1,2}$} %{R. Hoyland$^{\orcidlink{0000-0001-5346-0519}}$,$^{1,2}$}
{A. Lasenby$^{\orcidlink{0000-0002-8208-6332}}$,$^{6,7}$} %{A. Lasenby$^{\orcidlink{0000-0002-8208-6332}}$,$^{6,7}$}
\newauthor
{E. Mart\'{i}nez-Gonz\'{a}lez$^{\orcidlink{0000-0002-0179-8590}}$,$^{8}$} %{E. Mart\'{i}nez-Gonzalez$^{\orcidlink{0000-0002-0179-8590}}$,$^{8}$}
L. Piccirillo,$^{12}$
{R. Rebolo$^{\orcidlink{0000-0003-3767-7085}}$,$^{1,2,13}$} %{R. Rebolo$^{\orcidlink{0000-0003-3767-7085}}$,$^{1,2,11}$}
D. Tramonte,$^{14,1,2}$
F. Vansyngel,$^{1,2}$
\newauthor
{P. Vielva$^{\orcidlink{0000-0003-0051-272X}}$,$^{8}$} %{P. Vielva$^{\orcidlink{0000-0003-0051-272X}}$,$^{8}$}
{R.~A. Watson$^{\orcidlink{0000-0002-5873-0124}}$,$^{12}$} %{R.~A. Watson$^{\orcidlink{0000-0002-5873-0124}}$,$^{12}$}
\\
% List of Institutions
$^{1}$Instituto de Astrof\'{i}sica de Canarias, E-38200 La Laguna, Tenerife, Spain\\
%
$^{2}$Departamento de Astrof\'{i}sica, Universidad de La Laguna, E-38206 La Laguna, Tenerife, Spain\\
%
$^{3}$Departamento de F\'{i}sica. Facultad de Ciencias. Universidad de C\'{o}rdoba. Campus de Rabanales, Edif. C2. Planta Baja.  E-14071 C\'{o}rdoba, Spain\\
%
$^{4}$
Imperial College London, Blackett Lab, Prince Consort Road, London SW7 2AZ, UK\\
%
$^{5}$Universidad de Cantabria, Departamento de Ingeniería de Comunicaciones, Edificio Ingenieria de Telecomunicación, \\ \quad Plaza de la Ciencia nº 1, 39005 Santander, Spain\\
%
$^{6}$Astrophysics Group, Cavendish Laboratory, University of Cambridge, 
J J Thomson Avenue, Cambridge CB3 0HE, UK\\
$^{7}$Kavli Institute for Cosmology, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
%
$^{8}$Instituto de F\'{\i}sica de Cantabria (IFCA), CSIC-Univ. de Cantabria, Avda. los
Castros, s/n, E-39005 Santander, Spain\\
%
$^{9}$Departamento de F\'{\i}sica Moderna, Universidad de Cantabria,
Avda. de los Castros s/n, 39005 Santander, Spain\\
%
$^{10}$CNRS-UCB International Research Laboratory, Centre Pierre Binétruy, IRL2007, CPB-IN2P3, Berkeley, CA 94720, USA\\
%
$^{11}$Institut d'Astrophysique de Paris, UMR 7095, CNRS \& Sorbonne Universit\'e, 98 bis boulevard Arago, 75014 Paris, France\\
%
$^{12}$Jodrell Bank Centre for Astrophysics, Alan Turing Building, Department of Physics \& Astronomy, School of Natural Sciences,\\ \quad The University of Manchester, Oxford Road, Manchester, M13 9PL, U.K. \\
%
$^{13}$Consejo Superior de Investigaciones Cient\'{i}ficas, E-28006
Madrid, Spain\\
%
$^{14}$Department of Physics, Xi'an Jiaotong-Liverpool University, 111 Ren'ai Road, \\ \quad Suzhou Dushu Lake Science and Education Innovation District, Suzhou Industrial Park, Suzhou 215123, P.R. China.
}