%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%%
%%
%\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
\documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{lipsum}  
\usepackage{placeins}
\usepackage{subcaption}
\usepackage{overpic}
\usepackage{url}
\usepackage[pdftex, pdftitle={Article}, pdfauthor={Author},colorlinks = true,allcolors = blue]{hyperref}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}
\journal{NIMA}

\begin{document}



\affiliation[UCR]{Department of Physics and Astronomy, University of California, Riverside, CA 92521, USA}
\affiliation[JLAB]{Thomas Jefferson National Accelerator Facility, Newport News, VA 23606, USA}



\author[UCR,JLAB]{Miguel Arratia\corref{correspondingauthor}}
\cortext[correspondingauthor]{Corresponding author}

\author[UCR]{Ryan Milton}
\author[UCR,JLAB]{Sebouh Paul}
\author[UCR]{Barak Schmookler}
\author[UCR]{Weibin Zhang}

\title{A Few-Degree Calorimeter for the future Electron-Ion Collider}



%\date{\today} 

\begin{abstract}
Measuring the region $0.1 < Q^{2} < 1.0$ GeV$^{2}$ is essential to support searches for gluon saturation at the future Electron-Ion Collider. Recent studies have revealed that covering this region at the highest beam energies is not feasible with current detector designs, resulting in the so-called $Q^{2}$ gap.  In this work, we present a design for the Few-Degree Calorimeter (FDC), which addresses this issue. The FDC uses SiPM-on-tile technology with tungsten absorber and covers the range of $-4.6 < \eta < -3.6$. It offers fine transverse and longitudinal granularity, along with excellent time resolution, enabling standalone electron tagging. Our design represents the first concrete solution to bridge the $Q^{2}$ gap at the EIC.

\end{abstract}




\maketitle
\newpage
\tableofcontents
%\newpage
\input{sections/Introduction}
\input{sections/DesignConstraints}
\input{sections/Design}
\input{sections/SimulatedPerformance}
\input{sections/Conclusions}


\section*{Acknowledgements} \label{sec:acknowledgements}
We would like to extend our sincere appreciation to the members of the California EIC consortium for their valuable feedback on the design and physics that motivated the FDC, with special recognition to Oleg Tsai, Farid Salazar, and Zhongbo Kang. Additionally, we are grateful to Elke-Caroline Aschenauer for her guidance regarding the current acceptance of the crystal ECAL in ePIC. 

This work was supported by MRPI program of the University of California Office of the President, award number 00010100. This work was supposed by DOE grant award number DE-SC0022324. S.P also acknowledges support from the Jefferson Lab EIC Center Fellowship. M.A acknowledges support through DOE Contract No. DE-AC05-06OR23177 under which Jefferson Science Associates, LLC operates the Thomas Jefferson National Accelerator Facility.
\renewcommand\refname{Bibliography}
\bibliographystyle{utphys} % or try abbrvnat or unsrtnat
\bibliography{bibio.bib} % refers to example.bib

\appendix
\end{document}