% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2018/03/10
%
\documentclass[runningheads]{llncs}

\pdfoutput=1
\usepackage[T1]{fontenc}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{listings}
\lstset{language=Pascal}



%%%%%%%%%%%%% My Packages %%%%%%%%%%%%%
\usepackage[colorlinks=true,linkcolor=green,citecolor=blue]{hyperref}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{anyfontsize}
\usepackage{amssymb}  % http://ctan.org/pkg/amssymb
\usepackage{booktabs} 
\usepackage{changepage}
\usepackage{float}
\usepackage{gensymb}
\usepackage{graphicx}
\usepackage[all]{hypcap}
\usepackage{ltablex}
\usepackage{mathtools}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{mwe}   % to get dummy images
\usepackage{pdflscape}
\usepackage{pifont}   % http://ctan.org/pkg/pifont
\usepackage{placeins}
\usepackage{rotating}
\usepackage{soul}
\usepackage{scalerel}
\usepackage{stackengine}
\usepackage{tabularx}
\usepackage{tabularray}
\usepackage{textcomp}
\usepackage{xcolor}

%%%%%%%%%%%%% My Macros %%%%%%%%%%%%%

\def \name{SwIPE}

\usepackage[mathscr]{euscript}
\DeclareSymbolFont{rsfs}{U}{rsfs}{m}{n}
\DeclareSymbolFontAlphabet{\mathscrsfs}{rsfs}

% \setlist{nosep, leftmargin=14pt}

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\Lagr}{\mathcal{L}}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
\newcommand\dunderline[3][-1pt]{{%
  \sbox0{#3}%
  \ooalign{\copy0\cr\rule[\dimexpr#1-#2\relax]{\wd0}{#2}}}}
\def\subsubsec#1{\noindent\scaleto{\underline{\textbf{#1}}.}{10.65pt}}
\def\subsubsec#1{\noindent\scaleto{\dunderline[-.75pt]{0.25pt}{\textbf{#1}}.}{7.6pt}}

\newcommand\tabbig[1][2cm]{\hspace*{#1}}
\newcommand\tabtiny[1][1mm]{\hspace*{#1}}


\newcommand{\algcomment}{\tabbig \color{gray} {\#} \color{black}}
\def\algcomments#1{\tabbig \color{gray!90!black!90} {\small \# #1} \color{black}}

\newlength{\blob}
\settowidth{\blob}{Mi}
\newlength{\nameblob}
\settowidth{\nameblob}{ResUNet2}


\def\ptext#1{\color{green!60!black!90} {\scaleto{(#1)}{6.5pt}} \color{black}}
\def\ntext#1{\color{red} {\scaleto{(#1)}{6.5pt}} \color{black}}
\def\sdtext#1{\color{black} {\scriptsize $\pm$ \hspace{-1.4mm} #1} \color{black}}

\renewcommand{\sectionautorefname}{\S \hspace{-1mm}}
\renewcommand{\subsectionautorefname}{\S \hspace{-1mm}}
\renewcommand{\subsubsectionautorefname}{\S \hspace{-1mm}}
\newcommand{\dsquare}{\hspace*{2pt}\topinset{$\square$}{$\square$}{2pt}{-2pt}}
\newcommand{\ssquare}{\topinset{$\square$}{$\square$}{0.1pt}{-0.1pt}}


%%%%%%%%%%%%% Document Start %%%%%%%%%%%%%


\begin{document}
%
% \title{Vector Prediction: a Surprisingly Robust Self-supervised 3D Pretraining Task for CT Segmentation}
\title{
SwIPE: Efficient and Robust Medical Image Segmentation with Implicit Patch Embeddings}
\titlerunning{\name}

% Non-anon Author List
\author{\vspace*{-0.5mm}
Yejia Zhang \and  
Pengfei Gu \and   
Nishchal Sapkota \and  
Danny Z. Chen     
}
%index{Zhang, Yejia}
%index{Gu, Pengfei}
%index{Sapkota, Nishchal}
%index{Chen, Danny}

\institute{\vspace*{-0.25mm}
University of Notre Dame, Notre Dame IN 46556, USA \\
\email{\{yzhang46,pgu,nsapkota,dchen\}@nd.edu}}
\authorrunning{Zhang et al.}



\maketitle            
\begin{abstract}  % 150 - 250 words
\vspace{-3.4mm}
Modern medical image segmentation methods primarily use \textit{discrete} representations in the form of rasterized masks to learn features and generate predictions. 
Although effective, this paradigm is spatially inflexible, scales poorly to higher-resolution images, and lacks direct understanding of object shapes. 
% To address these limitations, some recent works utilized implicit neural representations (INRs) to learn \textit{continuous} representations for segmentation, but often directly adopted components designed for 3D shape reconstruction. 
% These formulations also constrained themselves to either point-based or global contexts which lack contextual understanding or local fine-grained details, respectively --- both essential for accurate segmentation.
To address these limitations, some recent works utilized implicit neural representations (INRs) to learn \textit{continuous} representations for segmentation.
However, these methods often directly adopted components designed for 3D shape reconstruction. 
More importantly, these formulations were also constrained to either point-based or global contexts, lacking contextual understanding or local fine-grained details, respectively---both critical for accurate segmentation.
To remedy this, we propose a novel approach, \textbf{SwIPE} (\underline{S}egmentation \underline{w}ith \underline{I}mplicit \underline{P}atch \underline{E}mbeddings), that leverages the advantages of INRs and predicts shapes at the patch level---rather than at the point level or image level---to enable both accurate local boundary delineation and global shape coherence.
% by modeling shapes at an image patch level.
% maintaining fine-grained local information and global shape coherence.
Extensive evaluations on two tasks (2D polyp segmentation and 3D abdominal organ segmentation) show that SwIPE significantly improves over recent implicit approaches and outperforms state-of-the-art discrete methods with over 10x fewer parameters.
Our method also demonstrates superior data efficiency and improved robustness to data shifts across image resolutions and datasets.
Code is available on \href{https://github.com/charzharr/miccai23-swipe-implicit-segmentation}{Github}.

\vspace{-2.5mm}
\keywords{Medical Image Segmentation \and Deep Implicit Shape Representations \and Patch Embeddings \and Implicit Shape Regularization}
\end{abstract}



%%%%%%% ------------------------------------------------------------------------- %%%%%%%
%%%%%%% ------------------------------------------------------------------------- %%%%%%%

\input{sections/1_introduction.tex}
\input{sections/2_methodology.tex}
\input{sections/3_results.tex}
\input{sections/4_conclusions.tex}

\vspace*{-1mm}

\bibliographystyle{splncs04}
\bibliography{refs}

%%%%%%% ------------------------------------------------------------------------- %%%%%%%
%%%%%%% ------------------------------------------------------------------------- %%%%%%%




\end{document}

