\begin{filecontents}{ex_supplement.aux}
\relax 
\providecommand\hyper@newdestlabel[2]{}
\providecommand\HyperFirstAtBeginDocument{\AtBeginDocument}
\HyperFirstAtBeginDocument{\ifx\hyper@anchor\@undefined
	\global\let\oldcontentsline\contentsline
	\gdef\contentsline#1#2#3#4{\oldcontentsline{#1}{#2}{#3}}
	\global\let\oldnewlabel\newlabel
	\gdef\newlabel#1#2{\newlabelxx{#1}#2}
	\gdef\newlabelxx#1#2#3#4#5#6{\oldnewlabel{#1}{{#2}{#3}}}
	\AtEndDocument{\ifx\hyper@anchor\@undefined
		\let\contentsline\oldcontentsline
		\let\newlabel\oldnewlabel
		\fi}
	\fi}
\global\let\hyper@last\relax 
\gdef\HyperFirstAtBeginDocument#1{#1}
\providecommand\HyField@AuxAddToFields[1]{}
\providecommand\HyField@AuxAddToCoFields[2]{}
\newlabel{app:proofs}{{SM1}{SM1}{Proofs}{section.1}{}}
\newlabel{app:proofs@cref}{{[section][1][]SM1}{[SM1][1][]SM1}}
\@writefile{toc}{\contentsline {section}{\numberline {SM1}Proofs}{SM1}{section.1}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.1}Proof of \cref  {thm:ts_agnostic}}{SM1}{subsection.2}\protected@file@percent }
\@writefile{thm}{\contentsline {lemma}{{Lemma}{SM1.1}{}}{SM1}{theorem.3}\protected@file@percent }
\@writefile{thm}{\contentsline {proof}{{Proof}{1}{}}{SM1}{proof.4}\protected@file@percent }
\global\def\markiproofi{\proofbox }
\newlabel{lemma:Gy_symmetric}{{SM1.1}{SM1}{Proof of \cref {thm:ts_agnostic}}{proof.4}{}}
\newlabel{lemma:Gy_symmetric@cref}{{[lemma][1][1]SM1.1}{[SM1][1][]SM1}}
\@writefile{thm}{\contentsline {lemma}{{Lemma}{SM1.2}{}}{SM1}{theorem.5}\protected@file@percent }
\citation{bhatiaposdef}
\@writefile{thm}{\contentsline {proof}{{Proof}{2}{}}{SM2}{proof.6}\protected@file@percent }
\global\def\markiiproofii{\proofbox }
\newlabel{prop:gammaS_decomp}{{SM1.2}{SM2}{Proof of \cref {thm:ts_agnostic}}{proof.6}{}}
\newlabel{prop:gammaS_decomp@cref}{{[lemma][2][1]SM1.2}{[SM1][2][]SM2}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.2}Proof of \cref  {thm:affineinvariance}}{SM2}{subsection.7}\protected@file@percent }
\@writefile{toc}{\contentsline {subsubsection}{\numberline {SM1.2.1}Preliminaries}{SM2}{subsubsection.8}\protected@file@percent }
\@writefile{thm}{\contentsline {lemma}{{Lemma}{SM1.3}{}}{SM2}{theorem.9}\protected@file@percent }
\newlabel{eq:logequiv}{{SM1.1}{SM2}{Preliminaries}{equation.10}{}}
\newlabel{eq:logequiv@cref}{{[equation][1][1]SM1.1}{[SM1][2][]SM2}}
\@writefile{thm}{\contentsline {proof}{{Proof}{3}{}}{SM2}{proof.11}\protected@file@percent }
\newlabel{eq:logtilde}{{SM1.2}{SM2}{Preliminaries}{equation.12}{}}
\newlabel{eq:logtilde@cref}{{[equation][2][1]SM1.2}{[SM1][2][]SM2}}
\newlabel{lemma:logequiv}{{SM1.3}{SM3}{Preliminaries}{equation.12}{}}
\newlabel{lemma:logequiv@cref}{{[lemma][3][1]SM1.3}{[SM1][3][]SM3}}
\@writefile{thm}{\contentsline {corollary}{{Corollary}{SM1.4}{}}{SM3}{theorem.13}\protected@file@percent }
\@writefile{thm}{\contentsline {proof}{{Proof}{4}{}}{SM3}{proof.14}\protected@file@percent }
\global\def\markivproofi{\proofbox }
\newlabel{corr:logequiv_K}{{SM1.4}{SM3}{Preliminaries}{proof.14}{}}
\newlabel{corr:logequiv_K@cref}{{[corollary][4][1]SM1.4}{[SM1][3][]SM3}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {SM1.2.2}Main Result}{SM3}{subsubsection.15}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.3}Proof of \cref  {prop:mle}}{SM4}{subsection.16}\protected@file@percent }
\newlabel{eq:mdist_min_tsa}{{SM1.3}{SM4}{Proof of \cref {prop:mle}}{equation.17}{}}
\newlabel{eq:mdist_min_tsa@cref}{{[equation][3][1]SM1.3}{[SM1][4][]SM4}}
\newlabel{app:proof_nleq}{{SM1.4}{SM4}{Proof of \cref {prop:nleq}}{subsection.18}{}}
\newlabel{app:proof_nleq@cref}{{[subsection][4][1]SM1.4}{[SM1][4][]SM4}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.4}Proof of \cref  {prop:nleq}}{SM4}{subsection.18}\protected@file@percent }
\newlabel{eq:opt_blocks}{{SM1.4}{SM4}{Proof of \cref {prop:nleq}}{equation.19}{}}
\newlabel{eq:opt_blocks@cref}{{[equation][4][1]SM1.4}{[SM1][4][]SM4}}
\newlabel{eq:insert_calS}{{SM1.5}{SM4}{Proof of \cref {prop:nleq}}{equation.20}{}}
\newlabel{eq:insert_calS@cref}{{[equation][5][1]SM1.5}{[SM1][4][]SM4}}
\citation{lu2002inverses}
\newlabel{eq:Cinvs}{{SM1.6}{SM5}{Proof of \cref {prop:nleq}}{equation.21}{}}
\newlabel{eq:Cinvs@cref}{{[equation][6][1]SM1.6}{[SM1][5][]SM5}}
\newlabel{eq:nleq_calS}{{SM1.7}{SM5}{Proof of \cref {prop:nleq}}{equation.22}{}}
\newlabel{eq:nleq_calS@cref}{{[equation][7][1]SM1.7}{[SM1][5][]SM5}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.5}Proof of \cref  {prop:expectedMdist}}{SM5}{subsection.23}\protected@file@percent }
\citation{pennec2006intrinsic}
\newlabel{eq:mean_mdist_min}{{SM1.8}{SM6}{Proof of \cref {prop:expectedMdist}}{equation.24}{}}
\newlabel{eq:mean_mdist_min@cref}{{[equation][8][1]SM1.8}{[SM1][6][]SM6}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM1.6}Proof of \cref  {prop:BLUEs}}{SM6}{subsection.25}\protected@file@percent }
\newlabel{eq:euclidean_blue}{{SM1.9}{SM6}{Proof of \cref {prop:BLUEs}}{equation.26}{}}
\newlabel{eq:euclidean_blue@cref}{{[equation][9][1]SM1.9}{[SM1][6][]SM6}}
\newlabel{eq:euclidean_constraint_blue}{{SM1.10}{SM6}{Proof of \cref {prop:BLUEs}}{equation.27}{}}
\newlabel{eq:euclidean_constraint_blue@cref}{{[equation][10][1]SM1.10}{[SM1][6][]SM6}}
\newlabel{eq:euclidean_cv_B}{{SM1.11}{SM6}{Proof of \cref {prop:BLUEs}}{equation.28}{}}
\newlabel{eq:euclidean_cv_B@cref}{{[equation][11][1]SM1.11}{[SM1][6][]SM6}}
\newlabel{eq:affinvar_BLUE}{{SM1.12}{SM7}{Proof of \cref {prop:BLUEs}}{equation.29}{}}
\newlabel{eq:affinvar_BLUE@cref}{{[equation][12][1]SM1.12}{[SM1][7][]SM7}}
\citation{HeldEtAl1985}
\citation{CapetEtAl2008}
\newlabel{app:sqg}{{SM2}{SM8}{Supplement to \cref {sec:metricLearning}: metric-learning with the surface quasi-geostrophic equation}{section.30}{}}
\newlabel{app:sqg@cref}{{[section][2][]SM2}{[SM1][8][]SM8}}
\@writefile{toc}{\contentsline {section}{\numberline {SM2}Supplement to \cref  {sec:metricLearning}: metric-learning with the surface quasi-geostrophic equation}{SM8}{section.30}\protected@file@percent }
\@writefile{toc}{\contentsline {subsection}{\numberline {SM2.1}Experimental setup}{SM8}{subsection.31}\protected@file@percent }
\newlabel{eq:sqg_system}{{SM2.1}{SM8}{Experimental setup}{equation.32}{}}
\newlabel{eq:sqg_system@cref}{{[equation][1][2]SM2.1}{[SM1][8][]SM8}}
\@writefile{lof}{\contentsline {figure}{\numberline {SM1}{\ignorespaces Examples of buoyancy, evolving according to \cref  {eq:sqg_system}, at initial (top) and final time (bottom) for ${\bm  {\theta }}$ sampled from class $i = 0$ (left) and $i = 1$ (right). Observations consist of solution values at nine spatial locations in the domain, as depicted in plots (c) and (d). We use the observations to estimate a metric which will distinguish between solutions corresponding to ${\bm  {\theta }}$ sampled from class $i = 0$ and ${\bm  {\theta }}$ sampled from class $i = 1$. \relax }}{SM9}{figure.caption.33}\protected@file@percent }
\providecommand*\caption@xref[2]{\@setref\relax\@undefined{#1}}
\newlabel{fig:SQG_solution}{{SM1}{SM9}{Examples of buoyancy, evolving according to \cref {eq:sqg_system}, at initial (top) and final time (bottom) for $\bftheta $ sampled from class $i = 0$ (left) and $i = 1$ (right). Observations consist of solution values at nine spatial locations in the domain, as depicted in plots (c) and (d). We use the observations to estimate a metric which will distinguish between solutions corresponding to $\bftheta $ sampled from class $i = 0$ and $\bftheta $ sampled from class $i = 1$. \relax }{figure.caption.33}{}}
\newlabel{fig:SQG_solution@cref}{{[figure][1][]SM1}{[SM1][9][]SM9}}
\newlabel{app:sqg:addResults}{{SM2.2}{SM10}{Additional results}{subsection.34}{}}
\newlabel{app:sqg:addResults@cref}{{[subsection][2][2]SM2.2}{[SM1][9][]SM10}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM2.2}Additional results}{SM10}{subsection.34}\protected@file@percent }
\@writefile{lof}{\contentsline {figure}{\numberline {SM2}{\ignorespaces \textbf  {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat  \Gamma _0^{\rm  LF}$, $\hat  \Gamma _0^{\rm  EMF}$, $\hat  \Gamma _0^{\rm  LEMF}$, and $\hat  \Gamma _0^{\rm  MRMF}$ compared to that of $\hat  \Gamma _0^{\rm  HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat  \Gamma _0^{\rm  HF}$. \textbf  {Bottom:} Frobenius squared error histograms of $\hat  \Gamma _0^{\rm  LF}$ (left), $\hat  \Gamma _0^{\rm  EMF}$ (center), and $\hat  \Gamma _0^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _0^{\rm  MRMF}$, overlaid in blue. In the Frobenius metric $\hat  \Gamma _{\rm  0}^{\rm  EMF}$ is the best-performing estimator, which is to be expected, as $\hat  \Gamma _{\rm  0}^{\rm  EMF}$ is optimized to minimize Frobenius MSE. . \relax }}{SM10}{figure.caption.35}\protected@file@percent }
\newlabel{fig:Gamma0_fro}{{SM2}{SM10}{\textbf {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat \Gamma _0^{\rm LF}$, $\hat \Gamma _0^{\rm EMF}$, $\hat \Gamma _0^{\rm LEMF}$, and $\hat \Gamma _0^{\rm MRMF}$ compared to that of $\hat \Gamma _0^{\rm HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat \Gamma _0^{\rm HF}$. \textbf {Bottom:} Frobenius squared error histograms of $\hat \Gamma _0^{\rm LF}$ (left), $\hat \Gamma _0^{\rm EMF}$ (center), and $\hat \Gamma _0^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _0^{\rm MRMF}$, overlaid in blue. In the Frobenius metric $\hat \Gamma _{\rm 0}^{\rm EMF}$ is the best-performing estimator, which is to be expected, as $\hat \Gamma _{\rm 0}^{\rm EMF}$ is optimized to minimize Frobenius MSE. . \relax }{figure.caption.35}{}}
\newlabel{fig:Gamma0_fro@cref}{{[figure][2][]SM2}{[SM1][9][]SM10}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {SM2.2.1}Estimation of $\Gamma _0$}{SM10}{subsubsection.36}\protected@file@percent }
\@writefile{lof}{\contentsline {figure}{\numberline {SM3}{\ignorespaces \textbf  {Top:} Intrinsic squared error histograms corresponding to $\hat  \Gamma _0^{\rm  LF}$ (left), $\hat  \Gamma _0^{\rm  LEMF}$ (center), and $\hat  \Gamma _0^{\rm  MRMF}$ (right). Squared error histograms for $\hat  \Gamma _0^{\rm  HF}$ are overlaid in cyan for comparison. Reported changes in MSE are relative to $\hat  \Gamma _0^{\rm  HF}$. \textbf  {Bottom:} Intrinsic squared error histograms of $\hat  \Gamma _0^{\rm  LF}$ (left) and $\hat  \Gamma _0^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _0^{\rm  MRMF}$, overlaid in blue. Use of $\hat  \Gamma _0^{\rm  MRMF}$ results in an 31\% decrease in intrinsic MSE relative to that of $\hat  \Gamma _0^{\rm  LF}$ and a 76\% decrease relative to that of $\hat  \Gamma _0^{\rm  LEMF}$. We do not report results for $\hat  \Gamma _{0}^{\rm  EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 82.4\% of its realizations are indefinite. \relax }}{SM11}{figure.caption.37}\protected@file@percent }
\newlabel{fig:Gamma0_AI_LE}{{SM3}{SM11}{\textbf {Top:} Intrinsic squared error histograms corresponding to $\hat \Gamma _0^{\rm LF}$ (left), $\hat \Gamma _0^{\rm LEMF}$ (center), and $\hat \Gamma _0^{\rm MRMF}$ (right). Squared error histograms for $\hat \Gamma _0^{\rm HF}$ are overlaid in cyan for comparison. Reported changes in MSE are relative to $\hat \Gamma _0^{\rm HF}$. \textbf {Bottom:} Intrinsic squared error histograms of $\hat \Gamma _0^{\rm LF}$ (left) and $\hat \Gamma _0^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _0^{\rm MRMF}$, overlaid in blue. Use of $\hat \Gamma _0^{\rm MRMF}$ results in an 31\% decrease in intrinsic MSE relative to that of $\hat \Gamma _0^{\rm LF}$ and a 76\% decrease relative to that of $\hat \Gamma _0^{\rm LEMF}$. We do not report results for $\hat \Gamma _{0}^{\rm EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 82.4\% of its realizations are indefinite. \relax }{figure.caption.37}{}}
\newlabel{fig:Gamma0_AI_LE@cref}{{[figure][3][]SM3}{[SM1][11][]SM11}}
\@writefile{toc}{\contentsline {subsubsection}{\numberline {SM2.2.2}Estimation of $\Gamma _1$}{SM11}{subsubsection.38}\protected@file@percent }
\@writefile{lof}{\contentsline {figure}{\numberline {SM4}{\ignorespaces \textbf  {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat  \Gamma _1^{\rm  LF}$, $\hat  \Gamma _1^{\rm  EMF}$, $\hat  \Gamma _1^{\rm  LEMF}$, and $\hat  \Gamma _1^{\rm  MRMF}$ compared to that of $\hat  \Gamma _1^{\rm  HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat  \Gamma _1^{\rm  HF}$. \textbf  {Bottom:} Frobenius squared error histograms of $\hat  \Gamma _1^{\rm  LF}$ (left), $\hat  \Gamma _1^{\rm  EMF}$ (center), and $\hat  \Gamma _1^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _1^{\rm  MRMF}$, overlaid in blue. All four estimators obtain substantial decreases in MSE relative to $\hat  \Gamma _1^{\rm  HF}$, but, interestingly, in the Frobenius metric $\hat  \Gamma _1^{\rm  MRMF}$ achieves the smallest reduction. By contrast, $\hat  \Gamma _1^{\rm  MRMF}$ is the best-performing estimator in the intrinsic metric (\cref  {fig:Gamma1_AI_LE}). \relax }}{SM12}{figure.caption.39}\protected@file@percent }
\newlabel{fig:Gamma1_fro}{{SM4}{SM12}{\textbf {Top:} Frobenius squared error histograms corresponding to (from left to right) $\hat \Gamma _1^{\rm LF}$, $\hat \Gamma _1^{\rm EMF}$, $\hat \Gamma _1^{\rm LEMF}$, and $\hat \Gamma _1^{\rm MRMF}$ compared to that of $\hat \Gamma _1^{\rm HF}$, overlaid in cyan. Reported changes in MSE are relative to $\hat \Gamma _1^{\rm HF}$. \textbf {Bottom:} Frobenius squared error histograms of $\hat \Gamma _1^{\rm LF}$ (left), $\hat \Gamma _1^{\rm EMF}$ (center), and $\hat \Gamma _1^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _1^{\rm MRMF}$, overlaid in blue. All four estimators obtain substantial decreases in MSE relative to $\hat \Gamma _1^{\rm HF}$, but, interestingly, in the Frobenius metric $\hat \Gamma _1^{\rm MRMF}$ achieves the smallest reduction. By contrast, $\hat \Gamma _1^{\rm MRMF}$ is the best-performing estimator in the intrinsic metric (\cref {fig:Gamma1_AI_LE}). \relax }{figure.caption.39}{}}
\newlabel{fig:Gamma1_fro@cref}{{[figure][4][]SM4}{[SM1][11][]SM12}}
\@writefile{lof}{\contentsline {figure}{\numberline {SM5}{\ignorespaces \textbf  {Top:} Intrinsic squared error histograms corresponding to $\hat  \Gamma _1^{\rm  LF}$ (left), $\hat  \Gamma _1^{\rm  LEMF}$ (center), and $\hat  \Gamma _1^{\rm  MRMF}$ (right). Squared error histograms corresponding to $\hat  \Gamma _1^{\rm  HF}$ are overlaid in cyan on each plot for comparison. Changes in MSE are relative to $\hat  \Gamma _1^{\rm  HF}$. \textbf  {Bottom:} Intrinsic squared error histograms of $\hat  \Gamma _1^{\rm  LF}$ (left) and $\hat  \Gamma _1^{\rm  LEMF}$ (right) compared to that of $\hat  \Gamma _1^{\rm  MRMF}$, overlaid in blue. Use of $\hat  \Gamma _1^{\rm  MRMF}$ results in a 49\% decrease in intrinsic MSE relative to $\hat  \Gamma _1^{\rm  LF}$ and a 66\% decrease relative to $\hat  \Gamma _1^{\rm  LEMF}$. We do not report results for $\hat  \Gamma _{1}^{\rm  EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 67\% of its realizations are indefinite\relax }}{SM13}{figure.caption.40}\protected@file@percent }
\newlabel{fig:Gamma1_AI_LE}{{SM5}{SM13}{\textbf {Top:} Intrinsic squared error histograms corresponding to $\hat \Gamma _1^{\rm LF}$ (left), $\hat \Gamma _1^{\rm LEMF}$ (center), and $\hat \Gamma _1^{\rm MRMF}$ (right). Squared error histograms corresponding to $\hat \Gamma _1^{\rm HF}$ are overlaid in cyan on each plot for comparison. Changes in MSE are relative to $\hat \Gamma _1^{\rm HF}$. \textbf {Bottom:} Intrinsic squared error histograms of $\hat \Gamma _1^{\rm LF}$ (left) and $\hat \Gamma _1^{\rm LEMF}$ (right) compared to that of $\hat \Gamma _1^{\rm MRMF}$, overlaid in blue. Use of $\hat \Gamma _1^{\rm MRMF}$ results in a 49\% decrease in intrinsic MSE relative to $\hat \Gamma _1^{\rm LF}$ and a 66\% decrease relative to $\hat \Gamma _1^{\rm LEMF}$. We do not report results for $\hat \Gamma _{1}^{\rm EMF}$ in the intrinsic metric, which is only defined for SPD arguments, because 67\% of its realizations are indefinite\relax }{figure.caption.40}{}}
\newlabel{fig:Gamma1_AI_LE@cref}{{[figure][5][]SM5}{[SM1][12][]SM13}}
\newlabel{app:prodMan}{{SM3}{SM13}{SPD Product Manifolds}{section.41}{}}
\newlabel{app:prodMan@cref}{{[section][3][]SM3}{[SM1][13][]SM13}}
\@writefile{toc}{\contentsline {section}{\numberline {SM3}SPD Product Manifolds}{SM13}{section.41}\protected@file@percent }
\newlabel{app:prodMan_geom}{{SM3.1}{SM13}{Geometry}{subsection.42}{}}
\newlabel{app:prodMan_geom@cref}{{[subsection][1][3]SM3.1}{[SM1][13][]SM13}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM3.1}Geometry}{SM13}{subsection.42}\protected@file@percent }
\citation{pennec2006intrinsic}
\newlabel{eq:geodesicPnK}{{SM3.1}{SM14}{Geometry}{equation.43}{}}
\newlabel{eq:geodesicPnK@cref}{{[equation][1][3]SM3.1}{[SM1][14][]SM14}}
\newlabel{app:prodMan_stats}{{SM3.2}{SM14}{Statistics}{subsection.44}{}}
\newlabel{app:prodMan_stats@cref}{{[subsection][2][3]SM3.2}{[SM1][14][]SM14}}
\@writefile{toc}{\contentsline {subsection}{\numberline {SM3.2}Statistics}{SM14}{subsection.44}\protected@file@percent }
\newlabel{eq:prodman_mean}{{SM3.2}{SM14}{Statistics}{equation.45}{}}
\newlabel{eq:prodman_mean@cref}{{[equation][2][3]SM3.2}{[SM1][14][]SM14}}
\bibstyle{siamplain}
\bibdata{references}
\bibcite{bhatiaposdef}{1}
\bibcite{CapetEtAl2008}{2}
\bibcite{HeldEtAl1985}{3}
\bibcite{lu2002inverses}{4}
\bibcite{pennec2006intrinsic}{5}
\newlabel{eq:prodMan}{{SM3.3}{SM15}{Statistics}{equation.46}{}}
\newlabel{eq:prodMan@cref}{{[equation][3][3]SM3.3}{[SM1][15][]SM15}}
\gdef \@abspage@last{15}
\end{filecontents}