\looseness -1 We first show that the \subrl problem is hard to approximate in general.  
In particular, we establish a lower bound that implies \subrl cannot be approximated up to any constant factor in polynomial time, even for {\em deterministic} submodular MDPs. 
We prove this by reducing our problem to a known hard-to-approximate problem -- the submodular orienteering problem (\sop) \citep{chekuri_rg}.  
Since we focus on {\em deterministic} \smdp's, according to Proposition~\ref{prop:deterministicmarkov} and Proposition~\ref{prop:restatedetMDP}, it suffices to consider deterministic, Markovian policies. We now formally state the inapproximability result with proof given in \cref{apx: inapprox}.
\begin{restatable*}{theorm}{restateinapprox}\label{thm: inappx}
Let \opt be the optimal value for \subrl. Even for deterministic \smdp's, the \subrl problem is hard to approximate within a factor of $\Omega(\log^{1-\gamma} \opt)$ unless $\NP \subseteq \ZTIME(n^{polylog(n)})$. 
\end{restatable*}
Thus, under common assumptions in complexity theory \citep{chekuri_rg,Halperin2003inapprox}, the \subrl problem cannot be approximated in general to better than logarithmic factors. The significance of this result extends beyond submodular RL. As \subrl falls within the broader category of general non-Markovian reward functions, \cref{thm: inappx} implies that problems involving general set functions are similarly inapproximable, limited to logarithmic factors. 

Since the inapproximability result we present is worst-case in nature, it does not rule out that interesting \subrl problems remain practically solvable. In the next section, we introduce a general algorithm that can be efficiently implemented for any \subrl problem. In \cref{sec: experiments}, we demonstrate the effectiveness of the algorithm and its utility in an extensive experimental study involving submodular rewards. Additionally, in \cref{sec: theory}, we establish that our algorithm enjoys a constant factor approximation under stronger assumptions on the Markov chain.




