
\label{subsec:cdprfect}
 In this section, we study the relationship of the two problems \SCP\ and \CDC\ and introduce the notion of \textit{cd-perfect graphs}, which is defined below.
\begin{definition}[\textit{cd}-perfect graphs]
    An undirected graph $G$ is said to be $cd$-perfect if, for any induced subgraph $H$ of $G$, we have $\XCD(H)=\SC(H)$.
\end{definition}

  Recall from Definition~\ref{def:aux} that given a graph $G$, the auxiliary graph $G^*$ is the graph having $V(G^*)=V(G)$ and $E(G^*)=E(G^2)\setminus E(G)$. i.e. $E(G^*)= \{uv:u,v\in V(G)$ and $d_G(u,v)=2\}$. First, we study the parameters $\XCD(G)$ and $\SC(G)$ of a graph $G$, by relating them to some well-known graph parameters of the auxiliary graph $G^*$. This simple reduction has various interesting consequences. Since the results in this section heavily rely on $G^*$, throughout this section, we use the following definition of \textit{seperated-cluster}: a set $S\subseteq V(G)$ is a seperated-cluster, if for any pair of vertices $u,v\in V(G)$, we have $d_G(u,v)\neq 2$.




 The following proposition trivially follows from the definition of $G^*$.
\begin{proposition} \label{pro:omega_s}
    For any graph $G$, we have $\SC (G)=\alpha(G^*)$.
\end{proposition}

We then note some observations that further lead us to some necessary and sufficient conditions for $cd$-perfectness. Even though the derivations of these conditions are apparently simple, they have some interesting consequences for obtaining the results in the latter part of the section.
\begin{observation} \label{obs:cliquecover}
    For any graph $G$, we have $\XCD (G)\geq k(G^*)$.
\end{observation}
\begin{proof}
    Let $\XCD(G)=l$, where $I_1,I_2,\ldots, I_l$ denote the corresponding color classes of $G$. Let $j\in \{1,2,\ldots,l\}$. Then by the definition of $cd$- coloring, we have that $I_j$ is an independent set in $G$ and there exists a vertex $v_j\in V(G)$ such that $I_j\subseteq N_G[v_j]$. This implies that for any pair of vertices $u,v\in V(I_j)$, we have $d_G(u,v)=2$. This further implies that $I_j$ is a clique in $G^*$, and therefore $\{I_1,I_2,\ldots, I_l\}$ is a clique cover of $G^*$. Thus we have $\XCD (G)\geq k(G^*)$.
\end{proof}


Note that the reverse inequality of Observation~\ref{obs:cliquecover} is not necessarily true. For instance, consider the graph $C_6$ (an induced cycle on 6 vertices). It is not difficult to verify that $\XCD(C_6)=4$. But as $C_6^*$ is a disjoint union of two triangles, we have $k(C_6^*)=2<\XCD(C_6)$. In Theorem~\ref{thm:suff_cdclique}, we prove a sufficient condition for a graph to satisfy the equality in Observation~\ref{obs:cliquecover}. First, we define certain graphs. For this, consider the graph $C_6$. Since $C_6$ is bipartite, observe that $V(C_6)$ can be partitioned into two independent sets, say $A$ and $B$, where $\mid A\mid~ =~\mid B\mid~ =3$. We denote by $C_6^1$, $C_6^2$, and $C_6^3$, the graphs obtained by respectively adding \textit{1 edge, 2 edges, and 3 edges} to exactly one of the partite sets $A$ or $B$ of $C_6$ (see Figure~\ref{fig:c6-free}). Let $\mathcal{H}=\{C_6, C_6^1$, $C_6^2,C_6^3\}$ (refer Figure~\ref{fig:c6-free}). Now, we note a useful structural observation for graphs in $\mathcal{H}$. 
\begin{observation}\label{obs:structureH}
    For each $H\in \mathcal{H}$, we have an independent set $S\subseteq V(H)$ with $\mid S\mid~ =3$ such that the vertices in $S$ form an asteroidal-triple in $H$.
\end{observation}

Now, in the following lemma, we prove a property satisfied by $G^*$, when $G$ is restricted to be an $\mathcal{H}$-free graph. 
\begin{lemma}\label{lem:neighborhood}
Let $G$ be an $\mathcal{H}$-free graph and $G^*$ its corresponding auxiliary graph. Let $K$ be any clique in $G^*$. Then there exists a vertex $v_k\in V(G)$ such that $K\subseteq N_G(v_k)$.
\end{lemma}
\begin{proof}
    We prove this by induction on $\mid K\mid $. Consider the base case where $\mid K\mid ~=2$. Let $K=\{x,y\}$. Note that $K$ is a clique in $G^*$. By the definition of $G^*$, $xy\in E(G^*)$ implies that $d_G(x,y)=2$. i.e. there exists a vertex $v_k$ such that $x,y\in N_G(v_k)$. As this proves the base case, we can, therefore, assume that $\mid K\mid\geq~ 3$. By the induction hypothesis, we can also assume that the condition in the lemma holds for every clique, say $K'$ in $G^*$ with $\mid K'\mid ~<~\mid K\mid$. Let $x_1,x_2,x_3\in K$ (this is possible, since $\mid K\mid~ \geq 3)$. For $i\in \{1,2,3\}$, let $K_i$ denote the clique $K\setminus \{x_i\}$. By the induction hypothesis, there exists a vertex, say $v_i\in V(G)$, such that $K_i\subseteq N_G(v_i)$. Note that $K$ is an independent set in $G$ (as $K$ is a clique in $G^*$), and therefore $v_i\notin K$ for any $i\in \{1,2,3\}$. Also, in particular, we have $v_ix_j\in E(G)$ for each $i,j\in \{1,2,3\}$, where $i\neq j$. Suppose that $v_ix_i\notin E(G)$ for each $i\in \{1,2,3\}$.  This implies that $v_1$, $v_2$, and $v_3$ are all distinct vertices in $G$. Consider the induced subgraph, $H=G[\{x_1,x_2,x_3,v_1,v_2,v_3\}]$. Since $\{x_1,x_2,x_3\}$ is an independent set in $G$, we then have, 
    
\begin{align}{
   \textit{H}=    \left\lbrace \begin{aligned}
 C_6, & \text{ if \hspace{0.1cm}}\mid E(G[\{v_1,v_2,v_3\}])\mid=0 \\
C_6^1, & \text{ if \hspace{0.1cm}} \mid E(G[\{v_1,v_2,v_3\}])\mid=1 \\
 C_6^2, & \text{ if \hspace{0.1cm}} \mid E(G[\{v_1,v_2,v_3\}])\mid=2 \\
 C_6^3, & \text{ if \hspace{0.1cm}} \mid E(G[\{v_1,v_2,v_3\}])\mid =3
\end{aligned} \right .}
\end{align}


This contradicts the fact that $G$ is $\mathcal{H}$-free. Therefore, we can conclude that $v_ix_i\in E(G)$ for some $i\in \{1,2,3\}$. Then, as $K=K_i\cup\{x_i\}$, the vertex $v_i$ in $G$ has the property that $K\subseteq N_G(v_i)$. This proves the lemma.
\end{proof}

\begin{theorem}\label{thm:suff_cdclique}
Let $G$ be an $\mathcal{H}$-free graph and $G^*$ its corresponding auxiliary graph. Then $\XCD (G)= k(G^*)$.
\end{theorem}

\begin{proof}
By Observation~\ref{obs:cliquecover}, it is enough to show that $\XCD (G)\leq k(G^*)$. Let $k(G^*)=t$, and let $K_1,K_2,\ldots, K_t$ be a minimum sized clique cover of $G^*$. Since $G$ is $\mathcal{H}$-free, for each $j\in \{1,2,\ldots,t\}$, by Lemma~\ref{lem:neighborhood}, we have that there exists a vertex $v_j\in V(G)$ such that $K_j\subseteq N_G(v_j)$. As each set $K_j$ is an independent set in $G$ (since $K_j$ is a clique in $G^*$), we can now infer that each set $K_j$ is a valid color class for a $cd$-coloring of $G$. Since $V(G)$ is the disjoint union of the sets, $K_1,K_2,\ldots, K_t$, we can therefore conclude that $\XCD (G)\leq k(G^*)$. This proves the theorem.
 \end{proof}
Now Theorem~\ref{thm:suff_cdsubclique}, which provides a sufficient condition for a graph $G$ to have $\XCD(G)=\SC(G)$, is  immediate from Proposition~\ref{pro:omega_s} and Theorem~\ref{thm:suff_cdclique}.  The following corollary that provides a sufficient condition for a graph to be $cd$-perfect can also be easily inferred from Theorem~\ref{thm:suff_cdclique}.

 \begin{corollary}\label{corr:suffcdperfect}
     Let $G$ be an $\mathcal{H}$-free graph. If for any induced subgraph $H$ of $G$, $k(H^*)=\alpha(H^*)$ then $G$ is $cd$-perfect. Consequently, if $G$ is $\mathcal{H}$-free and $H^*$ is perfect for any induced subgraph $H$ of $G$, then $G$ is $cd$-perfect.
 \end{corollary}
 
 It is known in the literature that if $G$ is a co-bipartite graph, then $\XCD(G)=\SC(G)$~\cite{ShaluKiruCDTreeCobipar21}. As a consequence of Theorem~\ref{thm:suff_cdsubclique}, in the following corollary, we now have a simple and shorter proof for the same. 
 \begin{corollary}\label{corr:cobipartite}
    Let $G$ be a co-bipartite graph. Then $G$ is $cd$-perfect. 
\end{corollary}
\begin{proof}
Let $G=(A,B,E)$ be a co-bipartite graph. Since the class of co-bipartite graphs is closed under taking induced subgraphs, to prove the corollary, it is enough to show that  $\XCD(G)=\SC(G)$. Note that $\alpha(G)\leq 2$ (as any independent set in $G$ can have only at most one vertex from each of the sets $A$ and $B$). But for each graph $H\in \mathcal{H}$, we have an independent set of size 3 (by Observation~\ref{obs:structureH}). This implies that $G$ is $\mathcal{H}$-free. Since $G^*$ is a bipartite graph (as $G^*$ is a subgraph of complement of $G$), and therefore perfect, we then have $\XCD(G)=k(G^*)=\alpha(G^*)=\SC(G)$, by Theorem~\ref{thm:suff_cdsubclique}. 
\end{proof}

 \noindent\textbf{Note:}
Recall the family of graphs $\mathcal{H}=\{C_6,C_6^1,C_6^2,C_6^3\}$. 
Consider a graph $H\in \mathcal{H}$. It is not difficult to see that $\XCD(H)=3=\SC(H)$, if $H\neq C_6$, and $\XCD(H)=4>2=\SC(H)$, if $H=C_6$. This is why the sufficient condition for $cd$-perfectness given in Corollary~\ref{corr:suffcdperfect} is not a necessary condition. But naturally, if we consider the set $\mathcal{H'}=\{C_6^1,C_6^2,C_6^3\}$, we can obtain a necessary and sufficient condition for an $\mathcal{H'}$-free graph to be $cd$-perfect. This easy consequence (of the above observation, together with Theorem~\ref{thm:suff_cdclique}, Corollary~\ref{corr:suffcdperfect}, and Proposition~\ref{pro:omega_s}) is interesting on its own; because the class of $\mathcal{H'}$-free graphs forms a superclass of triangle-free graphs, $3K_1$-free graphs, etc, and therefore, the following corollary provides a characterization for these classes to be $cd$-perfect.

 \begin{corollary}
Let $G$ be an $\mathcal{H'}$-free graph. Then $G$ is $cd$-perfect if and only if $G$ is $C_6$-free and $k(H^*)=\alpha(H^*)$, for each induced subgraph $H$ of $G$. 
 \end{corollary}

\input{algo}
\input{c6-free}