\subsubsection*{\textbf{Proper interval graphs and $3K_1$-free graphs}}

%\label{subsec:Proper-interval graphs}
It is known that for the classes of proper interval graphs and $3K_1$-free graphs, the \CDC\ problem can be solved in $O(n^3)$ time~\cite{ShaluVSCDComplex20} (as they are sub-classes of claw-free graphs). We show that the \CDC\ problem can be solved in $O(n^{2.5})$ time for the above classes of graphs. 

\begin{observation} \label{obs:propertriangle}
Let $G$ be a proper interval graph or a $3K_1$-free graph. Then, $G^*$ is triangle-free.
\end{observation}

\begin{proof}
Let $G$ be a proper interval graph or a $3K_1$-free graph. For the sake of contradiction, assume that $K=\{a,b,c\}\subseteq V(G)=V(G^*)$ is a triangle in $G^*$. First, we claim that $G$ is $\mathcal{H}$-free. Note that for each graph $H\in \mathcal{H}$, we have an independent set of size 3, and therefore, a $3K_1$, and an asteroidal-triple (by Observation~\ref{obs:structureH}). Since $G$ is either a proper interval graph (which is AT-free) or a $3K_1$-free graph, we can therefore conclude that $G$ is an $\mathcal{H}$-free graph. 
%Now, as $K$ induces a triangle in $G^*$, we have that $K$ is an independent set in $G$ (by the definition of $G^*$). 
Since $K$ is a clique in $G^*$, we have $K$ is an independent set in $G$ (by the definition of $G^*$)  and as $G$ is $\mathcal{H}$-free, by Lemma~\ref{lem:neighborhood}, there exists a vertex $v_c\in V(G)$ such that $K\subseteq N_G(v_c)$. This implies that the graph induced by the set $K\cup \{v_c\}$ is a claw in $G$, a contradiction to the fact that $G$ is a proper interval graph or a $3K_1$-free graph (as they are both sub-classes of claw-free graphs).   
\end{proof}

Before evaluating the complexity of the \CDC\ problem for proper interval graphs and $3K_1$-free graphs, we note a few observations and a lemma. Note that for any graph $G$, we have $V(G^*)=V(G)=V(G^2)$, and $E(G^*)=E(G^2)\setminus E(G)$. Therefore, if $G^2$ can be computed in $O(n^2)$ time, then $G^*$ can also be computed in $O(n^2)$ time (as the subtraction of the adjacency matrices of $G^2$ and $G$ takes only $O(n^2)$ time). The first observation below is due to the result that the squares of proper interval graphs can be computed in $O(n^2)$ time~\cite{SatPMadPLinAlgoSqGr16}. 
\begin{observation}\label{obs:proper}
    For a proper interval graph $G$, the auxiliary graph $G^*$ can be computed in $O(n^2)$ time. 
\end{observation}
We now have some additional observations.
\begin{observation}\label{obs:cobipartite}
    For a co-bipartite graph $G$, the auxiliary graph $G^*$ can be computed in $O(n^2)$ time.
\end{observation}
\begin{proof}
    Let $G$ be a co-bipartite graph. Note that for any pair of vertices $u,v\in V(G)$, we have $uv\in E(G^2)$ if and only if $u\in A$, $v\in B$, and either $N_B(u)\neq \emptyset$ or $N_A(v)\neq \emptyset$ or both. This implies that $G^2$ can be constructed in $O(n^2)$ time, and so does $G^*$. \end{proof}
In the following lemma, we observe a structural property of $3K_1$-free graphs, which is crucial in proving Observation~\ref{obs:alpha} and is of independent interest.
\begin{lemma}\label{lem:nocobipatite}
    Let $G$ be a $3K_1$-free graph. If $G$ is not co-bipartite, then $G^2$ is a clique.
\end{lemma}
\begin{proof}
    
    Let $u$ and $v$ be any two non-adjacent vertices in $G$. To prove the lemma, it is enough to show that $uv\in E(G^2).$ Let $d_G(u)$ and $d_G(v)$ denote the degrees of the vertices $u$ and $v$ in $G$, respectively.  We first claim that $d_G(u)+d_G(v)\geq n-2$. Suppose not. Let $d_G(u)+d_G(v) < n-2$. This implies that $\mid N_G(u)\cup N_G(v)\cup\{u,v\}\mid <n$. This further implies that there exists a vertex $w\in V(G)$ such that $w$ is non-adjacent to both $u$ and $v$. Therefore, $\{u,v,w\}$ forms an independent set in $G$, which contradicts the fact that $G$ is $3K_1$-free. Therefore, we can assume that $d_G(u)+d_G(v)\geq n-2$. 

    
    Suppose that $d_G(u)+d_G(v)> n-2$. Then, as $\mid V(G)\setminus \{u,v\}\mid \leq n-2$, it should be the case that $N_G(u)\cap N_G(v)\neq \emptyset$. i.e. there exists a vertex $w\in V(G)$ such that $uw,wv\in E(G)$.  This implies that $uv\in E(G^2)$, and we are done. Now consider the case that $d_G(u)+d_G(v)= n-2$. Suppose that $N_G(u)\cap N_G(v)=\emptyset$. Then, as $\mid N_G(u)\cup N_G(v)\cup \{u,v\}\mid =n$, we have that $V(G)$ is a disjoint union of two sets $A=N_G(u)\cup \{u\}$ and $B=N_G(v)\cup \{v\}$. Since $G$ is not a co-bipartite graph, we can assume that at least one of the sets $N_G(u)$ or $N_G(v)$ contains at least two vertices in it.  Suppose that $\mid N_G(u)\mid \geq 2$ (respectively $\mid N_G(v)\mid \geq 2$). Now, if there exist vertices $x,y\in N_G(u)$ (respectively $N_G(v)$) such that $xy\notin E(G)$, then, as $x,y\notin N_G(v)$ (respectively $N_G(u)$), we have that $\{x,y,v\}$ (respectively $\{x,y,u\}$) forms an independent set in $G$. As this contradicts the fact that  $G$ is $3K_1$-free, we have that both the sets $N_G(u)$ and $N_G(v)$ form a clique. But then, this contradicts the fact that $G$ is not a co-bipartite graph (as in this case, $A$ and $B$ clearly form a two-clique partition of $V(G)$). Thus we can conclude that $N_G(u)\cap N_G(v)\neq \emptyset$, and therefore, $uv\in E(G^2)$. This completes the proof of lemma.
    \end{proof}
    \begin{observation} \label{obs:alpha}
        For a $3K_1$-free graph $G$, the auxiliary graph $G^*$ can be computed in $O(n^2)$ time.
    \end{observation}
  \vspace{-0.5cm}
    \begin{proof}
        Let $G$ be a $3K_1$-free graph. We can check whether $G$ is co-bipartite or not in $O(n^2)$ time (as it is enough to check whether $\overline{G}$ is bipartite or not). If $G$ is co-bipartite, then by Observation~\ref{obs:cobipartite}, we have that $G^*$ can be computed in $O(n^2)$ time. If $G$ is not co-bipartite, by  Lemma~\ref{lem:nocobipatite}, we have that $G^2$ is a clique, and therefore, the auxiliary graph $G^*$, can be computed in $O(n^2)$ time.
    \end{proof}
 Now we are ready to prove Theorem~\ref{thm:properalpha}.
    \vspace{0.5cm}
    
\noindent\textit{Proof  Theorem~\ref{thm:properalpha}}
Let $G$ be a proper interval graph or a $3K_1$-free graph. As noted in the proof of Observation~\ref{obs:propertriangle}, we have that $G$ is $\mathcal{H}$-free. Therefore, by Theorem~\ref{thm:suff_cdclique}, we have that $\XCD(G)=k(G^*)$, where $G^*$ is the corresponding auxiliary graph. By Observation~\ref{obs:propertriangle}, we have that $G^*$ is triangle-free. This implies that each clique in any clique cover of $G^*$ is either an edge or a single vertex. This further implies that $k(G^*)=n-\mid M\mid$, where $M$ denotes the size of the maximum cardinality matching in $G^*$. Note that if $G$ is a proper interval graph, then the auxiliary graph $G^*$ can be constructed in $O(n^2)$ time by Observation~\ref{obs:proper}, and if $G$ is a  $3K_1$-free graph, then the auxiliary graph $G^*$ can be constructed in $O(n^2)$ time by Observation~\ref{obs:alpha}. Also, the size of the maximum 
 cardinality matching in $G^*$ can be computed in $O(\sqrt{n}m')$ time~\cite{HopKarAlgoMaxMat73}, where $m'=\mid E(G^*)\mid \leq n^2$. Since the overall complexity is $O(n^{2.5})$, this proves the theorem. \qed


\begin{remark}
    As noted before, the time complexity of \CDC\ for the class of proper interval graphs and $3K_1$-free graphs provided in Theorem~\ref{thm:properalpha} is an improvement over the existing algorithms~\cite{ShaluVSCDComplex20} for the problem in the same graph classes. Clearly, the class of $3K_1$-free graphs is not $cd$-perfect, as \SCP\ is \NPC\ for $3K_1$-free graphs~\cite{ShaluSandhyaLowBound17}. %In Section~\ref{sec:interval}, we give a polynomial-time algorithm for \SCP\ problem for the class of interval graphs. 
    Further, we note that the parameters $\XCD$ and $\SC$ are not necessarily equal for proper interval graphs too (see an example in Figure~\ref{fig:proper_interval}). Therefore, the class of proper interval graphs and, in general, interval graphs are not $cd$-perfect. Now, regarding the complexity of \SCP\ problem on the class of proper interval graphs, we prove in Section~\ref{sec:interval} that \SCP\ is polynomial-time solvable even for its superclass, namely, interval graphs. 
\end{remark}


% Figure environment removed