\documentclass[pre,aps,twocolumn,showpacs]{revtex4-2}
\usepackage{graphicx,epstopdf}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{xcolor}
\usepackage{float}
\usepackage{amssymb,amsmath}
%\usepackage[font=small,skip=0pt]{caption}
%\usepackage[skip=1pt]{caption}
%\captionsetup{justification=raggedleft,singlelinecheck=false}
\setlength{\abovecaptionskip}{0pt plus 3pt minus 2pt}
%\newcommand{\angstrom}{\text{\normalfont\AA}}
\usepackage{tabularx}
\begin{document}
\title{Fine structures of Intrinsically Disordered Proteins}

\author{Swarnadeep Seth}
\author{Brandon Stine}
\author{Aniket Bhattacharya}
\altaffiliation[]
{Author to whom the correspondence should be addressed}
{}
\email{Aniket.Bhattacharya@ucf.edu}

\affiliation{Department of Physics, University of Central Florida, Orlando, Florida 32816-2385, USA}
\date{\today}
\begin{abstract}
We report simulation studies of 33 single intrinsically disordered
proteins (IDPs) using three similar coarse-grained (CG) bead-spring
models where interactions among different amino acids (represented as CG beads) are introduced
through a hydropathy matrix and additional screened Coulomb
interaction to account for charges of the amino acids along the chain
backbone. A comparison of our simulation studies of two CG models [Dignon {\em et al.}, PLOS
Comp. Biology, 14, 2018, Tesei {\em et al.} PNAS, 118, 2021] with two
different hydropathy scales (HPS, M3) for a larger set of amino acids
with the existing experimental data indicates an optimal interaction
parameter $\epsilon \simeq 0.18 - 0.2$ kCal/mole, as reported
previously, however, with a larger variation. We use these 
best-fit parameters to investigate both the universal aspects as well
as the fine structures of the individual IDPs whose
characteristics vary substantially in the charge-hydropathy
space by introducing additional metrics. First, we investigate the polymer specific scaling relations of
the IDPs in comparison to the universal scaling relations
[Bair {\em et al.}, J. Chem. Phys. {\bf 158}, 204902 (2023)] for the
homopolymers and demonstrate that (i) the scaled end-to-end distance
$\langle R_N^2\rangle/(2 L\ell_p)$ and the scaled transverse fluctuation $\tilde{l}^2_{\perp}=\sqrt{\langle{l_{\perp}^2}\rangle}/{L}$ 
are Gaussian. Then we introduce (ii) Wilson charge index
($\mathcal{W}$) that captures the essential features of charge
interactions and distribution in the sequence space, 
(iii) a skewness parameter ($\mathcal{S}$) that captures the finer
shape variation of the gyration radii distribution related to the
charge asymmetry. Finally, our study of the (iv) variation of $\langle R_g\rangle
$ as a function of salt concentration provides another important metric to bring
out finer characteristics of the IDPs which may carry relevant information for the origin of life.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\section{Introduction}
Intrinsically disordered proteins (IDPs) are low complexity proteins characterized by
a low proportion of hydrophobic residues
and a high content of polar and charged amino acids which make them
distinct from those which fold. IDPs lack well defined three-dimensional structures
and do not participate in forming $\alpha$-helices or $\beta$-strands,
and other secondary or tertiary structures~\cite{Best-COSB-2017}-\cite{Uversky2000}.
Since their discovery almost three decades ago the number of IDPs has
been growing at a steady rate~\cite{DisProt}. It is now known that almost 30\% of the
proteins are either IDPs or folded proteins have intrinsically
disordered regions (IDR) which play crucial roles in numerous biological processes, such as regulating
signaling pathways, helping in molecular recognition,
in initiating protein-protein interactions, and serve
as molecular switches~\cite{Ferrie, Giansanti}. 
The conformal flexibility of IDPs help mediate interactions with binding partners to 
form components of macromolecular complexes~\cite{Best_Nature2018,Schuler_NatCommn}. The flexibility and
often faster dynamics allow IDPs to bind to multiple different
proteins~\cite{Fung2018}. The IDP complexes~\cite{Best_Nature2018} has also been realized to play 
a central to the pathology of several degenerative diseases:
$\alpha$-synuclein (Parkinson’s disease), tau (Alzheimer’s disease), and IAPP
(Type II Diabetes)~\cite{Uversky2022}. \par
Evidently the studies of IDPs in the last two decades
has been an active area in various branches of science. Despite
tremendous growth and interest in studying IDPs - the discovery of new
IDPs and their fast dynamics made it difficult to study
experimentally using small angle X-Ray scattering (XAFS)~\cite{Svergun}, single molecule
Fourier resonance energy transfer (smFRET)~\cite{Schuler_PNAS2012, Schuler_Review, Schuler_JCP2018} and solution nuclear magnetic
resonance (sNMR)~\cite{Tompa2013} which have produced conflicting results. The
conformational information, such as end-to-end distance and gyration
radii are also available for a limited number of IDPs.
Thus, an integrative structural biology approach that
combines experimental techniques~\cite{expt_all}, such as NMR spectroscopy
and small-angle X-ray scattering, combined with computational
methods seem to be a practical and feasible approach
to unravel the conformational properties and interactions
of IDPs, shedding light on their structural ensembles.\par
Historically, computer simulation studies of CG models of polymers have played an important role
as a stand-alone discipline between theory and experiments
successfully predicting conformational and dynamic properties of
neutral and charged polymers. Similar studies have been
generalized for the IDPs taking into account different sizes, charges, and hydropathy index of the 20 different CG amino acid
beads~\cite{Ausbaugh,Mittal2018,Larsen2021,Pappu_Package,Thirumalai_2019}. The
first goal of this article is to enlarge the scope of validity of a
subset of these models (HPS and M3) by studying a large number of IDPs
and checking the convergence of the results obtained using other CG models~\cite{Pappu_Package,Thirumalai_2019}, as well as experimentally~\cite{COINT,FhuA,Weninger_SIC1,OPN,Gomes_SIC1,histatin5} as outlined below.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coarse grained models of IDPs}
One of the hallmarks of IDPs is their characterization using the
Uversky plot ~\cite{Uversky2000} where it has been shown 
that when the mean net absolute charge $\langle Q \rangle$
of a polypeptide chain at
neutral pH is plotted against the mean side chain hydropathy $\langle
H \rangle $, measured on the Kyte-Doolittle~\cite{Kyte}
hydrophobicity scale, a 
boundary line
\begin{equation}
\langle Q \rangle =
2.785\langle H \rangle - 1.151
\label{QH_plot}
\end{equation}
separates the compact (natively folded or
globular) and expanded (coil-like or pre-molten globular)
conformations~\cite{Uversky2000,Habchi}. Habchi {\em et al.}
~\cite{Habchi} improved
Eqn.~\ref{QH_plot} but the basic observation remains the same.
Evidently, a relatively large charge and a
small hydropathy ensure the extended structure of the IDPs. The simplicity has been appealing to build 
CG models of IDPs based on hydropathy, where the standard bead-spring model of a homopolymer has been generalized to incorporate the relative well depth between any two amino acids by through a hydropathy
matrix.~\cite{Ausbaugh}. 
Mittal and coworkers~\cite{Mittal2018,Mittal2022} have used this HPS model to compare the gyration
radii for several IDPs and found a reasonably good agreement. A
slightly different version has been used by Tesei~{\em et al.}~\cite{Larsen2021}. Unlike the HPS
models~\cite{Ausbaugh,Mittal2018,Larsen2021} where hydropathy is
introduced directly, other implicit solvent CG models have been used to study various properties of IDPs. Pappu and coworkers
developed a software called  ABSINTH (Assembly
of Biomolecules Studied by an Implicit, Novel, and Tunable
Hamiltonian) to study phase transitions in
IDPs~\cite{Pappu_Package}. Thirumalai and coworkers used another CG
model called SOP-IDP (self-organized polymer (SOP) coarse-grained
model for IDPs) with a finer level of granularity where,
except for Glycine and Alanine, the rest of the amino acid residues are
represented using a backbone bead and a side-chain (SC)
bead~\cite{Thirumalai_2019}. All these models are computationally more
efficient compared to the models with explicit solvent molecules and hence can be used to
study macromolecular condensates of IDPs leading to liquid-liquid phase
separation~\cite{Alberti-LLPS2019,Dorfmann-LLPS2019, McCarty-LLPS2019,Aksimentiev_JPCL2020,Muthukumar_MM2022} in membraneless organelles.\par
Studies of IDPs are relatively new and progressively more IDPs are
being cataloged~\cite{DisProt}. Compared to the models for the folded proteins, the
CG models of the IDPs are relatively new. Due to their flexibility and
faster dynamics, the experimental studies of the IDPs are relatively limited and often very difficult to interpret. Thus, studies of several CG models with convergence to the
experimental results is an important aspect of developing a better understanding of the statistical mechanical properties of the IDPs  which share properties of the polyelectrolytes and polyampholytes, but exhibit very different sequence-specific behaviors.
One of the goals of this paper is to critically examine the parameters of two hydropathy models of IDPs as
explained below by enlarging the scope of previous
work~\cite{Mittal2018}-\cite{Larsen2021}.
It is also worth noting,  and as we will provide specific examples in the result section, that IDPs sampled from different regions of the Charge-Hydropthay space may exhibit markedly different
characteristics. We have introduced new physically motivated metrics to analyze these fine structures of the IDPs
%\input{intro.tex}
% Figure environment removed
\subsection{HPS Model} 
In this article, we use two versions of the HPS model used previously~\cite{Mittal2018}-\cite{Larsen2021}.
The amino acid residues interact among themselves by a modified Van der Waals interaction potential, first introduced by Ashbaugh and Hatch~\cite{Ausbaugh} given by
\begin{align}
U_{VdW}\left(r_{ij}\right) = \begin{cases}
      U_{LJ}\left(r_{ij}\right) + (1-\lambda_{ij})\epsilon_{ij}, & \text{$r_{j} \leq 2^{\frac{1}{6}} \sigma_{ij}$}\\
      \lambda_{ij} U_{LJ}\left(r_{ij}\right), & \text{otherwise}
    \end{cases}       
\end{align}
where $U_{LJ}$ is the Lennard-Jones (LJ) potential,
\begin{align}
U_{LJ}\left(r_{ij}\right) = 4\epsilon_{ij} \left[\left(\frac{\sigma_{ij}}{r_{ij}}\right)^{12} - \left(\frac{\sigma_{ij}}{r_{ij}}\right)^6\right].
\end{align}
Here, $r_{ij}=\left | \vec{r}_i - \vec{r}_j \right|$ is the distance
between the amino acid beads with indices $i$ and $j$ positioned at $\vec{r}_i$
and $\vec{r}_j$,
$\epsilon_{ij}=\frac{1}{2}\left(\epsilon_i+\epsilon_j\right)$ and $\lambda_{ij}=\frac{1}{2}\left(\lambda_i+\lambda_j\right)$
are the strength of the van der Waal interaction and average hydropathy factor
between any two amino acids with indices $i$ and $j$. 
A harmonic bond potential
\begin{equation}
U_{b}\left(r_{ij}\right) = \frac{k_b}{2}\left(
  \frac{r_{ij}  - r^0_{ij}}{\sigma_{ij}} \right)^2.
\end{equation}
acts between two consecutive amino acid residues $i$ and
$j=i\pm1$. The spring constant $k_b$ = 8033 kJ/(mol$\cdot$nm$^2$) =
1920 kCal/(mol$\cdot$nm$^2$), and the equilibrium bond length is $r_0$
= 0.38 $nm$.\par
A screened-Coulomb (SC) interaction acts between any two charged amino
acids
\begin{equation}
  U_{SC}\left(r_{\alpha\beta}\right) =
  \frac{q_{\alpha}q_{\beta}e^2}{4\pi \epsilon_0 \epsilon_r}
  \left( \frac{e^{-\kappa r_{\alpha \beta}}}{r_{\alpha \beta}}\right) 
\end{equation}
where the indices $\alpha$ and $\beta$ refer to the subset of the indices $i$ and
$j$ for the charged amino acids, $\epsilon_r$ is the dielectric
constant of water, and $\kappa$ is the inverse Debye screening
length~\cite{Israel}.
The inverse Debye length $\kappa^{-1}$ is dependent on the ionic concentration (I) and expressed as
\begin{align}
\kappa^{-1} & = \sqrt{8 \pi l_B I N_A \times 10^{-24}} 
\end{align}
where $N_{A}$ is the Avogadro's number and $l_B$ is the Bjerrum length,
\begin{align}
l_B = \frac{e^2}{4\pi \epsilon_0 \epsilon_r k_BT}.
\end{align}
At higher temperatures, the dielectric constant typically decreases, which affects the strength of the electrostatic interactions. If the dielectric constant does not account for temperature effects, the electrostatic interactions may be overestimated, leading to unrealistic protein conformations or interactions. Hence, we implement the temperature-dependent dielectric constant of water as expressed by the empirical relation~\cite{Akerlof}
\begin{align}
\epsilon_r(T) = \frac{5321}{T} + 233.76 - 0.9297T  \nonumber \\
+ 1.147\times 10^{-3} T^2  - 8.292 \times 10^{-7} T^3. 
\end{align}
\subsection{M3 Model} 
Keeping the energy function the same as above, Tesei {\em et al.} used the Bayesian parameter-learning procedure to further optimize the hydropathy values and showed M3~\cite{Larsen2021} hydropathy scale performs better to produce radius of gyration values closer to the experiments. This M3 hydropathy scales of the amino acids are shown in $7^{th}$ column of Fig.~\ref{Model}(b). We used both the hydropathy scales HPS and M3 to study the properties of IDPs described in the subsequent sections.
\section{Results}
We studied 33 different IDPs with varying number of amino acids (N = 24 - 284) with
high net positive charge to high net negative charge (see the $6^{th}$ column of Table-~\ref{Table}). All these IDPs have been studied earlier by
different CG models.
Within the range of our studied IDPs, An16 is a
polyelectrolyte containing only six positively charged Histidine
residues, Nucleoporin153 which contains only uncharged residues, and the
rest of the 30 IDPs are polyampholytes. The table is sorted according
to their net charge, from highly positive in red to highly negative
shown in dark green and listed in the $6^{th}$ column. The first row of
the table lists K32 that contains 14~$\%$ Lysine (+1) and 4~$\%$
Aspartic acid (-1) which makes it highly positive. On the other hand,
the bottom row is ProTa-N that contains 20~$\%$ Glutamic acid (-1),
17~$\%$  Aspartic acid (-1) and 8~$\%$ Lysine (+1), which makes it
highly negative. We assign unique letter codes for each of the IDPs,
Greek letters $\alpha$-$\rho$ in the ascending order starting from
highly positively charged IDPs and in descending order with the alphabets
starting from the negatively charged IDPs. We present the experimental
conditions such as ionic concentration in mM and temperature at Kelvin
scale in the $4^{th}$ and $5^{th}$ columns respectively. The total number of amino acid residues is denoted by N in the $3^{rd}$ column and the $7^{th}$ column shows the total number of charge residues present in the IDPs. The experimental radius of gyration $R_g^{expt}$ values are listed in $11^{th}$ column. The
{\textcolor{red}{\huge$\circ$}},
{\textcolor{blue}{\large{$\square$}}}, and {\textcolor{green}{\large{$\Diamond$}}} in the 2nd column along with IDPs names denote the refs.~\cite{Thirumalai_2019},\cite{Mittal2018},\cite{Larsen2021} respectively from where these experimental values are obtained. The corresponding simulation $R_g$ values are listed in the $12^{th}$ column for the HPS scale, and the $14^{th}$ column for the M3 scale.
\par
\begin{table*}
\centering
% Figure removed
\caption{\small A comprehensive table shows the comparison between the experimental and the simulation values obtained using two different models. The 1st, 2nd, and 3rd columns denote the letter id, names, and number of amino acids in the IDPs. The symbols {\textcolor{red}{\Large{$\circ$}}}, {\textcolor{blue}{$\square$}},  and {\textcolor{green}{$\Diamond$}} in the 2nd column along with IDPs names are obtained from the list of IDPs considered in the previous studies by Baul~{\em et al.}~\cite{Thirumalai_2019}, Dignon~{\em et al.}~\cite{Mittal2018}, and Tesei~{\em et al.}~\cite{Larsen2021} respectively from where the experimental values and conditions are obtained. The 4th and 5th columns describe the experimental conditions: ionic concentration in mM and temperature in Kelvin scale respectively. The 6th and 7th columns represent the net charge and the number of charged residues. The 8th and 9th columns show the absolute charge per residue and net charge per residue as described in Eq.~\ref{q_definition}. The 10th column represents the fraction charge content~\cite{Pappu2010}. The experimental radius of gyrations of all the IDPs are presented on the 11th column. The 12th and 14th columns represent the simulation radius of gyration results obtained by the HPS hydropathy scale and the M3 scale for $\epsilon=0.18$, $\epsilon=0.3$ respectively where the MSE is obtained to be the least (see Fig.~\ref{Rg}). We show the percentage error in the 13th and 15th columns corresponding to HPS and M3 scale. The last column shows the area under the Wilson charge curve from Fig.~\ref{wilson_chg}.}
\label{Table}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Historically many hydropathy scales have been introduces to model the
properties of amino acids and provide a quantitative measure of the
hydrophilicity or hydrophobicity of amino acids based on
their propensity to reside in a water-soluble or water-insoluble
environment~\cite{Kyte,Engelman,Hopp, Eisenberg,Cornette}. Each of these scales assigns a numerical value to each amino acid, reflecting its hydrophobic or hydrophilic nature. The scores obtained from hydropathy scales are useful in predicting protein structure and function. Recently, specific hydropathy scales are employed to study the liquid–liquid phase separation (LLPS) behavior of IDPs. Dignon~{\em et al.} proposed HPS~\cite{Mittal2018} hydropathy scale where Proline and Phenylalanine are considered to be the most hydrophobic with $\lambda^{HPS}=1$ and Arginine is the least hydrophobic with $\lambda^{HPS}=0$. All the amino acids' hydropathy are scaled to fit in the range. Later Tesei {\em et al.} used the Bayesian parameter-learning procedure to further optimize the hydropathy values and showed M3~\cite{Larsen2021} hydropathy scale performs better to produce radius of gyration values closer to the experiments.
\par
We use two hydropathy scales HPS~\cite{Mittal2018} and
M3~\cite{Larsen2021} to study 33 IDPs using the coarse grained simulation method described in Sec.~II. In the CG model, only free
parameter to vary is the interaction strength $\epsilon$. We obtained
the simulation radius of gyration values $R_{g}^{HPS}$ and $R_{g}^{M3}$
corresponding to HPS and M3 hydropathy scales for different values of
$\epsilon$. In Fig.~\ref{Rg}, we show the scatter plots of the
experimental vs. simulation radius of gyration data for five different
values of $\epsilon$ ranging from 0.1-0.3 kcal/mol. The deviations of
the simulation $R_g$ values from the experimental values is characterized by mean square error (MSE) defined as 
\begin{align}
MSE = \frac{1}{N} \sum_{i=1}^{N}\left[ R_g^{expt} (i) - R_{g}^{k} (i) \right]^2
\end{align}
where, $N$ is the number of IDPs, and $k$ represents either HPS or M3 depending on the hydropathy scale. From the
scatter plots we find $\epsilon$ = 0.18 has the lowest error
(MSE=0.48) and the best fit for the HPS model. On the other hand for
M3 hydropathy scale, the lowest error (MSE=0.65) is obtained for
$\epsilon$ = 0.3. This results are consistent with the optimum
$\epsilon$ values obtained for HPS scale by Dignon~{\em et
  al.}~\cite{Mittal2018} and for M3 scale by Tesei~{\em et
  al.}~\cite{Larsen2021}. As the HPS hydropathy scale with
$\epsilon$=0.18 yield the best match with the experimental $R_g$ values, we use these parameters to further analyze the properties of
the IDPs and discussed in the subsequent sections.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Universal Scaling Properties of the IDPs}
Despite the fact the IDPs are mostly described as polyampholytes (PAs) or polyelectrolytes (PEs)~\cite{Everaers_PRL}, a  fraction of experimental and theoretical studies using the HPS model describe IDPs as Gaussian chains~\cite{Mittal2022}, while  in a recent publication, Thirumalai and coworkers using a two-bead CG model calculated the RMS
$R_g\equiv \sqrt{\langle R_g^2\rangle}$ and
the end-to-end distance $R_N\equiv \sqrt{ \langle R_N^2\rangle }$ and concluded that globally the IDPs 
described not as the Gaussian chains, but rather as fully flexible swollen chains that obey the Flory scaling  $R_g= aN^{0.59}$~\cite{Thirumalai_2023}. We investigate this point further to find out to what extent the properties of the IDPs are universal. 
From theoretical arguments following Schaefer~{\em
  et al.}~\cite{Pincus_MM_1980} and Nakanishi~\cite{Nakanishi_1987} it
is established 
that a proper description of a semi-flexible swollen chain characterized by a contour length $L$ and a persistence length $\ell_p$ in $d$ spatial dimensions is given by 
\begin{equation}
\sqrt {\langle R_N^2 \rangle} \simeq b_l^{\frac{d-2}{d+2}} N^{\frac{3}{d+2}}\ell_p^{\frac{1}{d+2}} = b_l^{\frac{d+1}{d+2}}\left( \frac{L}{b_l}\right)^{\nu}\ell_p^{\frac{1}{d+2}}. 
\label{Rn_EV}
\end{equation}
Here $N$ is the number of monomers of the chain so that
$L = (N-1)b_l \simeq Nb_l$ (for $N \gg 1 $), $b_l$ is the bond length between two
neighboring monomers, and the mean-field Flory exponent $\nu =
3/(d+2)$ in 2D = 0.75 and in 3D = 0.60 ($\approx 0.588$ actual) respectively. 
This EV chain accurate describes the limit $L/\ell_p >> 1$ and supersedes the Worm-like-chain model~\cite{Rubinstein} 
\begin{equation}
\frac{\langle R_N^2\rangle}{L^2} = \frac{2\ell_p}{L}\left(1-\frac{\ell_p}{L}[1-\exp(-L/\ell_p)]\right).
\label{WLC}
\end{equation}
which does not take into account the EV effect and hence saturates to $\langle R_N^2 \rangle = 2 L\ell_p)$ even when $L/\ell_p >> 1$. In a previous publication 
we have shown that scaled end-to-end distance $\langle R_N^2 \rangle/(2 L\ell_p)$ and
 the scaled transverse fluctuation $\sqrt{\langle{l_{\perp}^2}\rangle}/{L}$ as a
 function of $L/\ell_p$ collapse onto the same master curve~\cite{Universal1,Universal2} for all ratios of $L/\ell_p$ spanning rod to Gaussian and the EV limit. We would like to  discuss our findings for the IDPs in the context of these universal scaling plots (Fig.~\ref{Scaling}). \par
 Fig.~\ref{Scaling}(a) summarizes our results for the scaling exponent that shows that $\langle R_g\rangle \approx 0.4L^{0.5}$. For comparison we have also included a dashed line describing $\langle R_g\rangle \approx L^{0.588}$. This result shows that in the HPS models IDPs are described as Gaussian chains. This is also consistent with the slope of the straight line fit (red dashed line in Fig.~\ref{Scaling}(a)) that corresponds to the average bond length $~0.43$. \par
To get a clearer perspective we have calculated the length of the IDPs and compared the scaled $R_g$ for the IDPs with reference to the universal master plot for the homopolymers of different length $L$ and persistence lengths $l_p$ (blue circles) in Fig.~\ref{Scaling}(b). These data points will serve as a guide and help readers to visualize the deviation of the scaling properties of the IDPs from those of the semiflexible swollen homopolymer statistics.  
 All the IDPs fall below the EV region and overall lie along the WLC model (dashed magenta). Our conclusion is further strengthened by Fig.~\ref{Scaling}(c), where we find that the scaled transverse fluctuations are Gaussian.\par
It is worth noting though that on the basis of this plot finer classification of the IDs can be made. We note that a couple of IDPs such as CspTm, ERMTADn and ProTa-C fall {\em below} the WLC line indicating {\em compact globular structures}, while ProTa-N stays above the WLC line indicating an elongated conformation. These findings align with a previous study by Baul {\em et al.}~\cite{Thirumalai_2019} where they found most of the IDPs follow Gaussian statistics. 
This findings confirm the fact that despite varying degree of mass, Gaussian chains in th HPS models.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{wilson.tex}
\subsection{Wilson index $\cal{W}$  of the IDPs}
Now that we have demonstrated an approximate universal description of the IDPs in terms of the HPS model, we want to demonstrate the sequence specific features those make each IDP distinct and may exhibit very different behaviors from their homopolymer counterparts. Evidently, the charges present along the sequence play a crucial role in shaping the structure and dynamics of the IDPs. Out of  20 amino acids, only five of them carry a charge. Specifically, in the HPS model, ``R" and ``K" each has a $+1$ charge, ``H'' possesses a $+0.5$ charge, and ``D'' and ``E'' have charge of $-1$. However, the charges are randomly distributed along the chain backbone and therefore, IDPs in general can be classified either as PA or PE~\cite{Pappu2013,Pappu2014}. The abundance of highly charged amino acids directly contributes to the formation of IDPs inhibiting the establishment of stable three-dimensional structures. Extensive research has been conducted to study this phenomenon in the existing literature. Nonetheless, our study delves deeper to investigate the positional implications of the amino acid sequence in terms of Wilson index ($\cal{W}$) as described below.
\par
Unlike a homopolymer, an IDP can have varied degree of local stiffness and flexibility resulting the amino acids in different segments interacting with neighboring sequences even if they are far apart in the sequence space.
To capture these potential dynamical interactions, we employ the concept of Wilson Renormalization extensively used to study
the spin systems~\cite{SK-Ma}. This renormalization approach allows us to analyze the sequence of charges and their unfolding interactions, considering interactions up to the next nearest neighbor. Fig.~\ref{Wilson_schematics} illustrates a hypothetical example of a short IDP sequence ``ESRKRT'' of length 6, showcasing the presence of a negative charge at the beginning followed by three positive charges in the middle, and the remaining amino acids being neutral. To initiate the averaging procedure, we select a window of length n. The simplest case $\tilde{\mathcal{W}}(2)$, considers sliding averages of window length n=2 and denotes the next neighbor interactions. The window length for averaging can range from 2 to $N$, where $N$ represents the number of amino acids in the IDP sequence.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
For the general case of $\tilde{\mathcal{W}}(n)$, where n consecutive charges are averaged, the process begins by sliding an averaging window from one end of the sequence toward the other. After the first step of averaging, denoted as S1, we obtain a new sequence of length $N-n+1$, and use the new sequence to carry on the averaging procedure as, 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{subequations}
\begin{equation} 
S0:  \left[a_1, a_2, \dots , a_N \right] 
\end{equation} 
\begin{equation} 
S1:  \left[\frac{1}{n}\sum_{i=1}^{n} a_i,\; \frac{1}{n}\sum_{i=2}^{n+1} a_i, \dots, \; \frac{1}{n}\sum_{i=N-n+1}^{N} a_i\right]  
\end{equation} 
\begin{equation} 
SN:  \tilde{\mathcal{W}}(n) = \frac{1}{n}\sum_{i=1}^{n} a_i.
\end{equation} 
\end{subequations} 
We continue this procedure iteratively until we reach the final average value, represented as $\tilde{\mathcal{W}}(n)$. If the length of the charge sequence becomes less than the window length $n$ during the averaging process, we terminate the procedure and calculate a global average to obtain $\tilde{\mathcal{W}}(n)$.
\par
These averaging procedure with varied window size $n \in [2,N]$ can effectively capture the combination of charge interactions at different length scale. One can show that $\tilde{\mathcal{W}}(2)$ consider binomial interactions among the charges and expressed as 
\begin{align}
\tilde{\mathcal{W}}(n=2) = \frac{1}{2^{N-1}} \sum_{m=0}^{N-1} \binom{N-1}m a_m.
\end{align} 
The higher-order window averaging considers interactions of varying magnitudes, which can have an impact on determining dynamic conformations of IDPs. In Fig.~\ref{wilson_chg} we explore $\tilde{\mathcal{W}}(n)$ for 12 IDPs with different total charges from highly positive (a) K32 (Q=22.5), (g) CspTm (Q=-2.0) to highly negatively charged IDP (l) ProTaN (Q=-43.0) as a function of normalized window length n/N. In the case of highly positively and negatively charged IDPs, the Wilson curves consistently remain above or below the zero line respectively. However, for IDPs with lower net charges, we sometimes observe the Wilson curve crossing from negative to positive in the case of (f) R15, (g) CspTm, and from positive to negative in the case of (j) $\alpha$-synuclein, and (K) OPN. The area under the Wilson curve is denoted by $\mathcal{W}=\sum_{n=2}^{N} \tilde{\mathcal{W}}(n)$ and listed in the 16$^{th}$ column of Table.-~\ref{Table}. It is conceivable that when plotted in normalized unit length scale IDPs with similar Wilson charge $\tilde{\mathcal{W}}(n)$ will behave the same way and thus, can be used as their fingerprints.\par
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{lp.tex}
\subsection{Charge patches and the local persistence length}
Presence of charge patches introduce varying degree of local stiffness along the chain backbone. During the BD simulation 
use a discrete chain and the persistence length is calculated from~\cite{Rubinstein}
\begin{equation}
  \ell_p/\sigma = -\frac{1}{\ln\left(\cos\theta_i\right)},
\label{lp_sim}
  \end{equation}
  where $\theta_i$ is the angle is the angle between two bond vectors connecting the $i^{th}$ bead to the $(i\pm1)^{th}$ beads~\cite{Universal2}. We have checked that for a homopolymer chain this matches well with the continuum description of persistence length~\cite{Landau}
\begin{equation}
\ell_p/\sigma = \kappa/k_BT \quad {\rm (3D)}.
    \label{lp_3d}
  \end{equation}
IDPs with very similar net charge can have markedly different distribution of charges. An IDP containing correlated charge patches will have increased chain stiffness along that region that will affect its conformations and dynamics.
To demonstrate this, we calculate the local persistence length ($l_p$)
along the chain using Eqn.~\ref{lp_sim} for a few IDPs shown in
Fig.~\ref{lp_IDP}. For example, CspTm has sparsely distributed charged
residues with less net charge compared to ProTa-N containing mostly negatively charged residues in patches, and we observe increase in $l_p$ on those regions. The electrostatic repulsion among the same charge residues make the chain locally stiffer and possibly has a deeper effect in their participation in  biophysical processes.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{skew.tex}
\subsection{Skewness factor ($\mathcal{S}$) of the radius of gyration}
The variation of the chain persistence length due to different charge species along the chain backbone is manifested in the shapes of the corresponding gyration radii that we measure in terms of a skewness factor $\mathcal{S}$.  The skewness parameter $\mathcal{S} $ is obtained by fitting $P\left(\bar{R}_g\right)$ with the exponentially-modified Gaussian distribution (exponnorm)~\cite{exponnorm} given by 
\begin{equation}
f(x,K) = \frac{1}{2K}\exp\left(\frac{1}{2K^2}-\frac{x}{K} \right)\rm{erfc}\left(-\frac{x-1/k}{\sqrt{2}} \right)
\end{equation}
where $x$ is a real number, $K > 0$ and erfc is the
complementary error function. 
The skewness parameter $\mathcal{S}$ can be obtained as 
\begin{equation}
\mathcal{S} = 2 l^3 \frac{K+2}{(K+3)\sqrt{K}},
\end{equation}
where $l$ and $K$ correspond to the shape parameter, and the scale parameter of the exponnorm distribution. We observe that the shapes of the distribution of the gyration radii vary from being near Gaussian to exponentially modified Gaussian distribution (that exhibits a tail) as shown in Fig.~\ref{skewness} where we 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
plot the distribution $P\left(\bar{R}_g\right) $ of scaled radius of gyration radii $\bar{R}_g= \sqrt{R_g^2}/ \langle \sqrt{R_g^2}\rangle $. By fitting these histograms with exponentially modified Gaussian distributions shown as the colored solid lines in Fig.~\ref{skewness}, we find the skewness $\mathcal{S}$ for the each case. Fig.~\ref{skewness} confirms that most of the IDPs have long exponential tails ($\cal{S}\ge$ 1.0) such as CspTm, FhuA, hCyp, $\alpha$-synuclein, sNase, ACTR, K32, OPN, and SH4UD.
A few IDPs CoINT, ProTa-C, and HST5 have distribution shaped near Gaussian. 
Finally the highly charged IDP ProTa-N is observed to have almost perfect Gaussian distribution with $\cal{S} \le$ 0.5. Moreover, for the highly skewed distributions the peaks shift towards the left that signifies the median is smaller than the mean and there is a propensity of these IDPs to expand occasionally. This skewness parameter can be utilized a classifier to segregate the IDPs into three categories that characterize the propensity of expansion.
\par
A pertinent question is if the skewness is correlated to the charge content of the IDPs. In a previous study, Pappu {\em et al.}~\cite{Pappu2013} demonstrated that radius of gyration depends on the charge asymmetry parameter $f^{*} = \frac{(f^+-f^-)^2}{f^++f^-}$, where $f^+/f^-$ is the net positive/negative charge per residue of an IDP. Here we demonstrate that the charge asymmetry parameter $f^{*}$ correlates inversely with the skewness parameter  $\mathcal{S}$ shown in Fig.~\ref{skewness}(n). A high charge asymmetry uniformly extends the polymer leading to a lower value of $\mathcal{S}$. In particular for ProtaN which has the largest value of $f^*$, the skewness parameter $\mathcal{S} \rightarrow 0$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{salt.tex}
\subsection{Chain conformations and Ionic Concentration}
Solvent conditions, such as pH, temperature,
ionic strength, and the presence of specific molecules, can
significantly influence the conformations and hence the behaviors of
the IDPs, particularly in a cellular environment. The robustness of
the IDPs under external conditions can also be associated with the
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure environment removed
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
origin of life. Previous experimental studies
~\cite{Ueda2010,Schuler2010,Hoffmann} and simulation studies using CG
models~\cite{Reddy,Wohl} have revealed 
conformational changes and salt-induced phase transition and looked at
the liquid-liquid phase transitions in IDPs. IDPs are described either
as PEs or PAs with varying amounts of net charge~\cite{Pappu2010}. Thus, it is
conceivable that screening will affect the conformational aspects in a
significant way. Intuitively one can understand the behavior by using the idea of screening. The IDPs those are PE, an increase in salt
concentration will screen the net charge reducing the electrostatic
repulsion and hence by an large, all the PEs with a net positive or 
negative charge will have reduced gyration radii as a function of
increased screening. The case of PAs is a bit more subtle depending on an IDP's not only the net charge per residue $q_{net}$, but the fraction of the residues that are charged $q_{abs}$
as defined below.
\begin{equation}
  q_{net} = \frac{||Q_{+}|-|Q_{-}||}{N} \quad {\rm and} \quad q_{abs} = \frac{|Q_{+}|+|Q_{-}|}{N}
\label{q_definition}
\end{equation} 
Here, $Q_{+}$, $Q_{-}$, and $N$ represent the total positive and negative charges, and the number of amino acids in the IDP.  For the PA the loss/gain in electrostatic energy and entropy ultimately controls the show.
We have made an extensive study of the dependence of gyration radii of the 33 IDPs (listed in Table-~\ref{Table}) on salt concentration) under physiological conditions ranging from 0-300 mM  shown in Fig.~\ref{i_quads}. The IDPs can be placed on any one of the four quadrants (I, II, III, and iV) of $(q_{abs}, q_{net})$  to study their dependency on salt concentration (Fig.~\ref{i_quads}(a)).
Based on the values of $(q_{abs}, q_{net})$, two decision boundary lines $q_{abs}=0.275$ and $q_{net}=0.13$ place the IDPs into four subclasses.  Fig.~\ref{i_quads}(a) displays scatter plots of the 33 IDPs classified into four quadrants, represented by blue, green, orange, and red symbols corresponding to the I, II, III, and IV quadrants, respectively. For each quadrant,
a plot of the saturation values at each concentration is used to plot $\sqrt{R_g^2/R_g^2(0)}-1$ as a function of ionic concentration, where $R_g(0)$ corresponds to the radius of gyration under ion-free conditions.
Quadrant-I and IV are easy to understand. 
A strong PA, such as ProtaN lies in the quadrant-I as expected. But other PAs (OPN, ProTa-C, HST5) with large $q_{net}$ and $q_{abs}$ belong here. In this case, as the salt concentration increases, charge screening occurs, leading to a decrease in their radii of gyrations. This condition holds when only one type of charged residue is abundant in number.
On the other hand, in quadrant IV, $q_{abs}$ is high, but $q_{net}$ is low, corresponding to a situation where there is a higher number of charged residues, yet they are almost equal in numbers.
As both types of charges are present, at low salt concentration, the attraction between opposite charges reduces their radius of gyration due to electrostatic interactions. However, with increasing salt concentration, the charge screening effect comes into play, and the strength of electrostatic attraction among the oppositely charged residues decreases. Consequently, we observe a swelling of the IDPs, leading to a higher radius of gyration. 13 IDPs belong to this category.
In quadrant II and III, the $q_{abs}$ value is low, indicating a low content of charged residues. In quadrant II, we find that p53 is the only IDP out of the 33 that falls into this category but has a high value of $q_{net}$. This pathological case is characterized by having only 17 negative charge residues (GLU and ASP) and two positively charged residues (ARG and LYS). Due to the charge screening effect mostly on the negatively charged residues, it can be inferred that the radius of gyration will decrease and that is indeed true as observed from the plot.
In quadrant III, the $q_{net}$ is low corresponding to IDPs that have less net charge per residue. We find 15 IDPs belong to this category. Out of which gyration radii of hCyp, FhuA, and K10 increase while K19, K18, k27, K17, K32, and K16 decrease as a function of salt concentration. On the other hand, the remaining 5 IDPs namely Protein-L, SH4UD, An16, Nucleoporin153, and CoINT are robust to the variation of ionic concentration as they are mostly low charge containing IDPs. 
The segregation of IDPs into four subsections unravels insights about their responses to salt concentration and provides a framework to classify other unknown proteins based on how they will behave under a wide range of salt solutions.
\par
We further studied the accompanying variation in the shape of the distribution of the gyration radii by monitoring the skewness factor $\mathcal{S}$ as progressively more screening is introduced for the reason discussed in section D. Some examples are shown Fig.~\ref{i_quads}(c)-(h).  The skewness of the distributions for SIC1 for 10 mM, 100 mM, and 300 mM ionic concentration changes from 1.51, 1.75, and 1.24 respectively, and they span a larger conformational space. On the other hand, for ProTa-N  while the gyration radii decrease at higher salt concentrations implying they become more compact without altering the distribution shape. We also observe that gyration radii for a few IDPs 
(Protein-L, SH4UD, An16, Nucleoporin153, and CoINT) in Fig.~\ref{i_quads}(a) remain unaffected within the low salt limit of our study. With the change in the salt concentration, our simulation studies show that the degree of alteration in the shape of IDPs is different. The shape deformation is drastic in SIC1 compared to ProTa-N.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{conclusion.tex}
\subsection{Summary and Outlook}
In conclusion, we used two different CG models (HPS \& M3) to study both universal and fine structures of 33 IDPs and compared our results with available experimental results as well as simulation results for the same IDPs using other CG models. Our systematic  studies of a larger set of IDPs with fairly disparate level of absolute and net charge 
($q_{abs}$, $q_{net}$), and net hydropathy add many interesting characteristics to those studied previously using a similar models. Our larger set of IDPs converge on the interaction parameter $\epsilon=0.18$ with some variability. However, this expanded dataset establishes a more robust and reliable framework for studying IDPs in bulk. A natural question that has been addressed in the community that if sequence specificity makes every IDP distinct from each other, or they share some universal characteristics of homopolymers described by Flory's theory. We have been able to address both the issues. A comparison of the scaled end-to-end distance and transverse fluctuations in reference to our recently established universal results, we observe that IDPs studied here are described better by  Gaussian chains rather self-avoiding chains. The experimental results converge well with the simulation results. A soft interaction potential $\epsilon=0.18$ may be responsible for this. \par
We then study in detail how the absolute and net charge per residue ($q_{abs}$, $q_{net}$) manifest themselves in finer characteristics of the IDPs. We come up with several new metrics those reveal the uniqueness of each IDP, yet leaves room for making further classification of IDPs in different categories. The first one is the Wilson index $\mathcal{W}$ that on a normalized unit length scale demonstrates the uniqueness of each IDP
and hence can be used as their fingerprints. Likewise, we demonstrate how the charge patches control the local stiffness and hence the overall conformations of the IDPs that we further characterize by introducing a skewness index $\mathcal{S}$. We find that $\mathcal{S}$ interpolates from a low value to a larger value ($\mathcal{W} \rightarrow 0$ for a Gaussian distribution and large for a distribution with an exponential tail ) and further relate 
$\mathcal{S}$ to the the charge asymmetry parameter $f^*$ introduced by Das and Pappu~\cite{Pappu2013} to note that they are inversely correlated.\par
An important classification of the IDPs emerges from the study of salt dependence of the conformations of the IDPs. We find that IDPs exhibit very different characteristics and can be broadly placed in four different region in the ($q_{abs}, q_{net}$) space.\par
We conclude with some comments which may promote further studies to perfect the CG models. We and many others used isotropic radius of gyration as the sole physical quantity for comparison as this is the mostly available from the experiments.  The CG model can be refined by introducing other quantities.  For example, Wohl {\em et.al}~\cite{Wohl} studied  salting-out effect on the liquid–liquid phase separation (LLPS) of IDPs by introducing a salt-dependent term into the hydropathy used in the HPS model.
Maity {\em et al.}~\cite{Reddy} introduced Molecular Transfer Model to study the Salt-Induced Transitions. In the low concentrations of salts ($\le$ 1M) IDP conformations are affected by the degree of screening of electrostatic interactions of the charged residues and are independent of the specific salt identity which is likely the regime that we have studied. However, at high concentrations, salts affect IDP conformations through salt-specific Hofmeister effects~\cite{Capp2013,Pegram2010}. Thus, our studies will be useful in refining the existing HPS models for a wider range of parameter space.
\par
We note that some of the IDPs remain unaffected with the variation of salt concentration and thus can be compared with the behavior of other simpler amino acids identified and studied in the context of the origin of life~\cite{Origin_life}. 
We believe studies of IDPs using a variety of CG models open up several exciting avenues for future research, allowing for a deeper understanding of the unique properties and behavior of IDPs.
%\input{summary.tex}
\section{Acknowledgments}
All computations were carried out using STOKES High-Performance Computing Cluster at UCF.
\vfill
\input{references.tex}
\end{document}
