\documentclass{article}
\usepackage{newton3p}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{algorithmic}

\usepackage{amsmath,amssymb,amsthm,enumerate,mathrsfs}
\usepackage{cite}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{assum}{Assumption}[section]
\newtheorem{algo}[theorem]{Algorithm}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{algorithm}{Algorithm}[section]
\usepackage{algorithmic}


\numberwithin{equation}{section}

%
%%%%% page layout %%%%%
\setlength\topmargin{-12pt}% -10pt
\setlength\headheight{21.6pt}% 18pt
\setlength\headsep{16.8pt}% 14pt

%%%
\setlength\textheight{20.8cm}% B5 = 528pt
\setlength\textwidth{14cm}%  B5 = 348pt
%%%


%%%%\shorttitle{Newton's Method}
%%%%\shortauthor{C. T. Kelley}





\begin{document}
\makeatletter



\begin{center}
\large{\bf Newton's Method in Three Precisions}
\end{center}\vspace{5mm}
\begin{center}
\textsc{
C. T. Kelley\\
North Carolina State University\\
Department of Mathematics\\
Box 8205, Raleigh, NC 27695-8205, USA\\
Tim\_Kelley@ncsu.edu
}\end{center}


\vspace{2mm}


\footnotesize{
\noindent\begin{minipage}{14cm}
{\bf Abstract:}
We describe a three precision variant of Newton's method for nonlinear 
equations. We evaluate the nonlinear residual in double precision, store
the Jacobian matrix in single precision, and solve the equation for the 
Newton step with iterative refinement with a factorization in half precision.
We analyze the method as an inexact Newton method. This analysis shows that,
except for very poorly conditioned Jacobians,
the number of nonlinear iterations needed is the same that one would get if
one stored and factored the Jacobian in double precision. In many
ill-conditioned cases one can use the low precision factorization as a
preconditioner for a GMRES iteration. That approach can recover fast
convergence of the nonlinear iteration.
We present an example to illustrate the results.
\end{minipage}
 \\[5mm]
\noindent\begin{minipage}{14cm}
{\bf Dedication:}
To Masao Fukushima on his 75th birthday, with thanks for his many contributions to optimization.
\end{minipage}
}

\noindent{\bf Keywords:} {Newton's Method, Iterative Refinement, 
Mixed-Precision Algorithms}

\noindent{\bf Mathematics Subject Classification:
65H10, % Nonlinear Algebraic or Transcendental Equations: Systems of equations
65F05, % Numerical Linear Algebra: Direct Methods for Linear Systems
65F10, % Numerical Linear Algebra: Iterative Methods for Linear Systems
45G10, % Integral Equations: other nonlinear integral equations
}


\hbox to14cm{\hrulefill}\par


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%


\input{intro_Newton3P}

\input{Three_Precision_Newton3P}

\input{examples_Newton3P}

\clearpage

\section{Acknowledgments}
This work was partially supported by
%
%CEMeNT
US Department of Energy grant DE-NA003967
%
and National Science Foundation Grant
% NSF AA
DMS-1906446.


\bibliographystyle{siamplain}
\bibliography{newton3p}

%\begin{thebibliography}{99}
% Reference smaple:  http://www.ybook.co.jp/pjo-aim.pdf
%\bibitem{} 
%\end{thebibliography}


\end{document}
