% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bell1988contraction}{}}%
Bell, James H, and Rabindra D Mehta. 1988. {``Contraction Design for
Small Low-Speed Wind Tunnels.''}

\leavevmode\vadjust pre{\hypertarget{ref-blake2017mechanics}{}}%
Blake, William K. 2017. \emph{Mechanics of Flow-Induced Sound and
Vibration, Volume 2: Complex Flow-Structure Interactions}. Academic
press.

\leavevmode\vadjust pre{\hypertarget{ref-caiazzo2023effect}{}}%
Caiazzo, A, S Pargal, H Wu, M Sanjosé, J Yuan, and S Moreau. 2023. {``On
the Effect of Adverse Pressure Gradients on Wall-Pressure Statistics in
a Controlled-Diffusion Aerofoil Turbulent Boundary Layer.''}
\emph{Journal of Fluid Mechanics} 960: A17.

\leavevmode\vadjust pre{\hypertarget{ref-choi1990space}{}}%
Choi, Haecheon, and Parviz Moin. 1990. {``On the Space-Time
Characteristics of Wall-Pressure Fluctuations.''} \emph{Physics of
Fluids A: Fluid Dynamics} 2 (8): 1450--60.

\leavevmode\vadjust pre{\hypertarget{ref-chung2010large}{}}%
Chung, Daniel, and Beverley J Mckeon. 2010. {``Large-Eddy Simulation of
Large-Scale Structures in Long Channel Flow.''} \emph{Journal of Fluid
Mechanics} 661: 341--64.

\leavevmode\vadjust pre{\hypertarget{ref-churchfield2012numerical}{}}%
Churchfield, Matthew J, Sang Lee, John Michalakes, and Patrick J
Moriarty. 2012. {``A Numerical Study of the Effects of Atmospheric and
Wake Turbulence on Wind Turbine Dynamics.''} \emph{Journal of
Turbulence}, no. 13: N14.

\leavevmode\vadjust pre{\hypertarget{ref-comte1971simple}{}}%
Comte-Bellot, Genevieve, and Stanley Corrsin. 1971. {``Simple Eulerian
Time Correlation of Full-and Narrow-Band Velocity Signals in
Grid-Generated,`isotropic'turbulence.''} \emph{Journal of Fluid
Mechanics} 48 (2): 273--337.

\leavevmode\vadjust pre{\hypertarget{ref-connell2007flapping}{}}%
Connell, Benjamin SH, and Dick KP Yue. 2007. {``Flapping Dynamics of a
Flag in a Uniform Stream.''} \emph{Journal of Fluid Mechanics} 581:
33--67.

\leavevmode\vadjust pre{\hypertarget{ref-de2001fluides}{}}%
De Langre, Emmanuel. 2001. \emph{Fluides Et Solides}. Editions Ecole
Polytechnique.

\leavevmode\vadjust pre{\hypertarget{ref-de2008effects}{}}%
---------. 2008. {``Effects of Wind on Plants.''} \emph{Annu. Rev. Fluid
Mech.} 40: 141--68.

\leavevmode\vadjust pre{\hypertarget{ref-del2009estimation}{}}%
Del Alamo, Juan C, and Javier Jiménez. 2009. {``Estimation of Turbulent
Convection Velocities and Corrections to {T}aylor's Approximation.''}
\emph{Journal of Fluid Mechanics} 640: 5--26.

\leavevmode\vadjust pre{\hypertarget{ref-Dinkelacker_1977}{}}%
Dinkelacker, A., M. Hessel, G. E. A. Meier, and G. Schewe. 1977.
{``Investigation of Pressure Fluctuations Beneath a Turbulent Boundary
Layer by Means of an Optical Method.''} \emph{Phys. Of Fluids} 20.

\leavevmode\vadjust pre{\hypertarget{ref-Gayout_2021}{}}%
Gayout, A., M. Bourgoin, and N. Plihon. 2021. {``Rare Event-Triggered
Transitions in Aerodynamic Bifurcation.''} \emph{Phys. Rev. Lett.} 126
(104501).

\leavevmode\vadjust pre{\hypertarget{ref-goldschmidt1981turbulent}{}}%
Goldschmidt, VW, MF Young, and ES Ott. 1981. {``Turbulent Convective
Velocities (Broadband and Wavenumber Dependent) in a Plane Jet.''}
\emph{Journal of Fluid Mechanics} 105: 327--45.

\leavevmode\vadjust pre{\hypertarget{ref-He_2017}{}}%
He, G., G. Jin, and Y. Yang. 2017. {``Space-Time Correlations and
Dynamic Coupling in Turbulent Flows.''} \emph{Annu. Rev. Fluid Mech.}
49.

\leavevmode\vadjust pre{\hypertarget{ref-hussain1981measurements}{}}%
Hussain, AKMF, and AR Clark. 1981. {``Measurements of
Wavenumber-Celerity Spectrum in Plane and Axisymmetric Jets.''}
\emph{AIAA Journal} 19 (1): 51--55.

\leavevmode\vadjust pre{\hypertarget{ref-jimenez2018coherent}{}}%
Jiménez, Javier. 2018. {``Coherent Structures in Wall-Bounded
Turbulence.''} \emph{Journal of Fluid Mechanics} 842: P1.

\leavevmode\vadjust pre{\hypertarget{ref-technoramaF}{}}%
Kahn, Ned. 2002. {``Technorama Facade.''}
\url{https://nedkahn.com/portfolio/technorama-facade/}.

\leavevmode\vadjust pre{\hypertarget{ref-digitizedF}{}}%
---------. 2005. {``Digitized Field.''}
\url{https://nedkahn.com/portfolio/digitized-field/}.

\leavevmode\vadjust pre{\hypertarget{ref-glacialF}{}}%
---------. 2006. {``Glacial Facade.''}
\url{https://nedkahn.com/portfolio/glacial-facade/}.

\leavevmode\vadjust pre{\hypertarget{ref-ProjectL}{}}%
---------. 2014. {``Project Lions.''}
\url{https://nedkahn.com/portfolio/project-lions/}.

\leavevmode\vadjust pre{\hypertarget{ref-kolmogorov1941local}{}}%
Kolmogorov, Andrey Nikolaevich. 1941. {``The Local Structure of
Turbulence in Incompressible Viscous Fluid for Very Large Reynolds.''}
\emph{Numbers. In Dokl. Akad. Nauk SSSR} 30: 301.

\leavevmode\vadjust pre{\hypertarget{ref-moin2009revisiting}{}}%
Moin, P. 2009. {``Revisiting {T}aylor's Hypothesis.''} \emph{Journal of
Fluid Mechanics} 640: 1--4.

\leavevmode\vadjust pre{\hypertarget{ref-nove2020effect}{}}%
Nové-Josserand, C, S Perrard, A Lozano-Durán, Michael Benzaquen, M
Rabaud, and F Moisy. 2020. {``Effect of a Weak Current on Wind-Generated
Waves in the Wrinkle Regime.''} \emph{Physical Review Fluids} 5 (12):
124801.

\leavevmode\vadjust pre{\hypertarget{ref-paquier2016viscosity}{}}%
Paquier, Anna, Frederic Moisy, and Marc Rabaud. 2016. {``Viscosity
Effects in Wind Wave Generation.''} \emph{Physical Review Fluids} 1 (8):
083901.

\leavevmode\vadjust pre{\hypertarget{ref-perrard2019turbulent}{}}%
Perrard, Stéphane, Adrián Lozano-Durán, Marc Rabaud, Michael Benzaquen,
and Frédéric Moisy. 2019. {``Turbulent Windprint on a Liquid Surface.''}
\emph{Journal of Fluid Mechanics} 873: 1020--54.

\leavevmode\vadjust pre{\hypertarget{ref-phillips1957generation}{}}%
Phillips, Owen M. 1957. {``On the Generation of Waves by Turbulent
Wind.''} \emph{Journal of Fluid Mechanics} 2 (5): 417--45.

\leavevmode\vadjust pre{\hypertarget{ref-Pope_2000}{}}%
Pope, Stephen B. 2000. \emph{Turbulent Flows}. Cambridge University
Press.

\leavevmode\vadjust pre{\hypertarget{ref-porte2020wind}{}}%
Porté-Agel, Fernando, Majid Bastankhah, and Sina Shamsoddin. 2020.
{``Wind-Turbine and Wind-Farm Flows: A Review.''} \emph{Boundary-Layer
Meteorology} 174 (1): 1--59.

\leavevmode\vadjust pre{\hypertarget{ref-ramananarivo2014propulsion}{}}%
Ramananarivo, Sophie. 2014. {``Propulsion Biomim{é}tique de Structures
{é}lastiques.''} PhD thesis, Universit{é} Paris-Diderot-Paris VII.

\leavevmode\vadjust pre{\hypertarget{ref-ristroph2008anomalous}{}}%
Ristroph, Leif, and Jun Zhang. 2008. {``Anomalous Hydrodynamic Drafting
of Interacting Flapping Flags.''} \emph{Physical Review Letters} 101
(19): 194502.

\leavevmode\vadjust pre{\hypertarget{ref-riviere2024bubble}{}}%
Rivière, Aliénor, Kamel Abahri, and Stéphane Perrard. 2024. {``Bubble
Shape Oscillations in a Turbulent Environment.''} \emph{arXiv Preprint
arXiv:2407.16545}.

\leavevmode\vadjust pre{\hypertarget{ref-shelley2011flapping}{}}%
Shelley, Michael J, and Jun Zhang. 2011. {``Flapping and Bending Bodies
Interacting with Fluid Flows.''} \emph{Annual Review of Fluid Mechanics}
43: 449--65.

\leavevmode\vadjust pre{\hypertarget{ref-sorensen2002wind}{}}%
Sørensen, Poul, Anca D Hansen, and Pedro André Carvalho Rosas. 2002.
{``Wind Models for Simulation of Power Fluctuations from Wind Farms.''}
\emph{Journal of Wind Engineering and Industrial Aerodynamics} 90
(12-15): 1381--1402.

\leavevmode\vadjust pre{\hypertarget{ref-taylor1938spectrum}{}}%
Taylor, Geoffrey Ingram. 1938. {``The Spectrum of Turbulence.''}
\emph{Proceedings of the Royal Society of London. Series A-Mathematical
and Physical Sciences} 164 (919): 476--90.

\leavevmode\vadjust pre{\hypertarget{ref-towne2020resolvent}{}}%
Towne, Aaron, Adrián Lozano-Durán, and Xiang Yang. 2020.
{``Resolvent-Based Estimation of Space--Time Flow Statistics.''}
\emph{Journal of Fluid Mechanics} 883: A17.

\leavevmode\vadjust pre{\hypertarget{ref-vassilicos2015dissipation}{}}%
Vassilicos, J Christos. 2015. {``Dissipation in Turbulent Flows.''}
\emph{Annual Review of Fluid Mechanics} 47: 95--114.

\leavevmode\vadjust pre{\hypertarget{ref-veers2019grand}{}}%
Veers, Paul, Katherine Dykes, Eric Lantz, Stephan Barth, Carlo L
Bottasso, Ola Carlson, Andrew Clifton, et al. 2019. {``Grand Challenges
in the Science of Wind Energy.''} \emph{Science} 366 (6464): eaau2027.

\leavevmode\vadjust pre{\hypertarget{ref-vermeer2003wind}{}}%
Vermeer, LJ, Jens Nørkær Sørensen, and Antonio Crespo. 2003. {``Wind
Turbine Wake Aerodynamics.''} \emph{Progress in Aerospace Sciences} 39
(6-7): 467--510.

\leavevmode\vadjust pre{\hypertarget{ref-wetz2023analyses}{}}%
Wetz, Tamino, Josef Zink, Jens Bange, and Norman Wildmann. 2023.
{``Analyses of Spatial Correlation and Coherence in ABL Flow with a
Fleet of UAS.''} \emph{Boundary-Layer Meteorology} 187 (3): 673--701.

\leavevmode\vadjust pre{\hypertarget{ref-willmarth1962measurements}{}}%
Willmarth, William W, and Charles Edward Wooldridge. 1962.
{``Measurements of the Fluctuating Pressure at the Wall Beneath a Thick
Turbulent Boundary Layer.''} \emph{Journal of Fluid Mechanics} 14 (2):
187--210.

\leavevmode\vadjust pre{\hypertarget{ref-wills1964convection}{}}%
Wills, JAB. 1964. {``On Convection Velocities in Turbulent Shear
Flows.''} \emph{Journal of Fluid Mechanics} 20 (3): 417--32.

\end{CSLReferences}

\end{document}
