\newcommand{\red}[1]{\textcolor{red}{ #1}}
\newcommand{\blue}[1]{\textcolor{blue}{ #1}}
\newcommand{\green}[1]{\textcolor{black}{ #1}}
\renewcommand{\baselinestretch}{1}
\newcommand{\yanyue}[1]{\textcolor{blue}{#1}}

\documentclass[9pt, conference]{IEEEtran}
%\documentclass[]{IEEEtran}
\usepackage{balance}
\input{misc/customize}


\begin{document}

\title{A Life-Cycle Energy and Inventory Analysis of Adiabatic Quantum-Flux-Parametron Circuits}
\author{
Masoud Zabihi, Yanyue Xie, Zhengang Li, Peiyan Dong, Geng Yuan, Olivia Chen, Massoud Pedram, Yanzhi Wang\\
%Northeastern University, 360 Huntington Ave, Boston, MA 02115
}

\maketitle
\begin{abstract}
The production process of superconductive integrated circuits is complex and consumes significant amounts of resources and energy. Therefore, it is crucial to evaluate the environmental impact of this emerging technology. An attractive option for the next generation of superconductive technology is Adiabatic Quantum-Flux-Parametron (AQFP) devices. This study is the first to present a comprehensive process-based life-cycle assessment (LCA) and inventory analysis of AQFP integrated circuits. To generate relevant outcomes, we conduct a comparative LCA that included the bulk CMOS technology. The inventory analysis considered the manufacturing, assembly, and use phases of the circuits. To ensure a fair assessment, we choose the 32-bit AQFP RISC-V single-core processor as the reference functional unit and compare its performance with that of a CMOS counterpart. Our findings reveal that the AQFP processor consumes several orders of magnitude less energy during the use phase than its CMOS counterpart. Consequently, the total life cycle energy (which encompasses manufacturing and assembly energies) of AQFP integrated circuits improves at least by two orders of magnitude.




\makeatletter
\renewcommand*{\@makefnmark}{}
\makeatother
\end{abstract}
%\makeatletter{\renewcommand*{\@makefnmark}{}
%\footnotetext{* (equal contribution)}\makeatother}


\input{sec/intro}
\input{sec/back}
\input{sec/results_discussion}
\input{sec/conclusion}
%\input{sec/8-ack}

\bibliographystyle{misc/ieeetr2}
\bibliography{misc/bibfile}
%misc/cram,misc/main.bib,misc/pim.bib}

%\input{sec/9-appendix}

\clearpage
%\input{sec/10-supplementary_material}

\end{document}
