\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{iccv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{csquotes}
\usepackage{verbatim}
\usepackage{color,soul}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{datetime2}
\usepackage{bm}
\usepackage{microtype}      % microtypography
\usepackage{dcolumn}        % Align table columns on decimal point
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{enumitem}
\usepackage{float}
\usepackage{stfloats}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers,sort,compress]{natbib}
\usepackage{amsthm}
\usepackage{subfiles}
\usepackage{adjustbox}
\usepackage{subcaption}
\usepackage{makecell}
\usepackage[normalem]{ulem}
\usepackage{caption}
% \usepackage{nopageno}
\usepackage[flushmargin,para]{footmisc}
% \usepackage[pagebackref,breaklinks,colorlinks]{hyperref} % please import last
\usepackage[table]{xcolor}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{array}
\usepackage{arydshln} 
\usepackage{tabularx}
\usepackage{booktabs}

\usepackage{multirow}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcommand{\methodname}{JOTR\xspace}
\definecolor{lightgray}{gray}{0.97}
\definecolor{lightblue}{rgb}{0.93,0.95,1.0}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
% \iccvfinalcopy

\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

\iccvfinalcopy % *** Uncomment this line for the final submission

\def\iccvPaperID{2019} % *** Enter the ICCV Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
% \ificcvfinal\pagestyle{empty}\fi

\begin{document}
\title{JOTR: 3D Joint Contrastive Learning with Transformers for \\ Occluded Human Mesh Recovery}
\author{
		Jiahao Li$^{1,2*}$, Zongxin Yang$^{1}$, Xiaohan Wang$^1$, Jianxin Ma$^2$, Chang Zhou$^2$, Yi Yang$^1$ \\
		$^1$ ReLER, CCAI, Zhejiang University \space \space \space $^2$ DAMO Academy, Alibaba Group \\
	}
\twocolumn[{%
		\renewcommand\twocolumn[1][]{#1}%
		\maketitle
		\begin{center}
			\newcommand{\teaserwidth}{\textwidth}
			\vspace{-6mm}
			\centerline{
				% Figure removed
			}
			\vspace{-0.1in}
			\captionof{figure}{
                (a) Current methods for human mesh recovery could be classified into two categories: AvgFeatReg~\cite{SPIN,HMR} and JointFeatReg~\cite{ROMP,zhang2021pymaf,3dCrwodNet}, which focus on improving 2D alignment by using average 2D features (feat.) for regression and employing sampled 2D joint feature for regression, respectively.
                In contrast, our proposed novel techniques (\ie, FusionFeatReg), fuse 2D and 3D features for regression to enhance both 2D and 3D alignment. (b) Moreover, to provide global supervision for the entire 3D space, we introduce a 3D joint contrastive learning method, which stands in contrast to previous approaches that solely apply 3D joints as local supervision.
			}
			\vspace{-4mm}
			\label{fig:fig_1}
		\end{center}%
}]
% \maketitle

%%%%%%%%% TITLE
% Remove page # from the first page of camera-ready.
% \ificcvfinal\thispagestyle{empty}\fi
\renewcommand{\thefootnote}{*}
\footnotetext{This work was done during Jiahao's internship at Alibaba.}
\input{sections/0_abstract}
\input{sections/1_introduction}
\input{sections/2_related_work}
\input{sections/3_method}
\input{sections/4_expirements}
\input{sections/5_conclusion}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{main}
}

\end{document}